---
params:
  partner: "IL_Kankakee District 111"
title: "`r paste0('Teaching Lab ', params$partner, ' Report')`"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  TeachingLab::TLDefault:
    css: styles.css
    fontawesome: false
    self_contained: true
    thumbnails: false
    lightbox: true
    gallery: false
    highlight: kate # Also can do tango
    number_sections: false
    includes:
      in_header: header.html
      after_body: footer.html
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(gt)
library(knitr)
library(scales)
library(stringr)
library(tidyr)
library(TeachingLab)

## Global options
opts_chunk$set(
  echo = FALSE,
  cache = FALSE,
  prompt = FALSE,
  tidy = TRUE,
  comment = NA,
  message = FALSE,
  warning = FALSE
)

final_session_survey_df <- readr::read_rds(here::here("data/SY22_23/end_of_session_survey_22_23.rds")) |>
  TeachingLab::neg_cond_filter(
    if_not_this = "All Partners",
    filter_this = params$partner,
    dat_filter = Site
  )

no_data_plot <- ggplot(tibble(text = "There was no data\nfor this site here.", x = 0, y = 0)) +
  geom_text(aes(label = text, x, y), fontface = "bold", family = "Calibri Bold", size = 10) +
  theme_void()
```

```{=html}
<script src="js/hideOutput.js"></script>
```

## Gender

<center>

```{r gender-summary}
gt_percent_n(
  df = final_session_survey_df,
  column = "Gender",
  custom_column_name = "Gender Identity", viz_type = sample(c("waffle", "pie", "treemap"),
    size = 1
  )
)
```

</center>

## Ethnicity

<center>

```{r ethnicity-summary}
gt_percent_n(
  df = final_session_survey_df,
  column = "Ethnicity",
  custom_column_name = "Ethnicity", viz_type = sample(c("waffle", "pie", "treemap"),
    size = 1
  )
)
```

</center>

## Content area

<center>

```{r content-area-summary}
gt_percent_n(
  df = final_session_survey_df,
  column = "Content area",
  custom_column_name = "Content area", viz_type = sample(c("waffle", "pie", "treemap"),
    size = 1
  )
)
```

</center>

## Race

<center>

```{r race-summary}
gt_percent_n(
  df = final_session_survey_df,
  column = "Race",
  custom_column_name = "Race", viz_type = sample(c("waffle", "pie", "treemap"),
    size = 1
  )
)
```

</center>

## Facilitator Quantitative Feedback

<center>

```{r quantitative-feedback}
plot_data <- final_session_survey_df |>
  select(
    `They demonstrated deep knowledge of the content they facilitated`,
    `They facilitated the content clearly`,
    `They effectively built a safe learning community`,
    `They were fully prepared for the session`,
    `They responded to the group’s needs`
  ) |>
  pivot_longer(everything(), names_to = "Question", values_to = "Response") |>
  drop_na(Response) |>
  dplyr::group_by(Question, Response) |>
  dplyr::count(sort = T) |>
  dplyr::ungroup() |>
  dplyr::group_by(Question) |>
  dplyr::mutate(
    Percent = 100 * n / sum(n),
    Question = str_wrap(Question, 30)
  )

if (exists("plot_data")) {
  fully_prepared <- plot_data |> TeachingLab::agree_strongly_agree(question = "They were fully prepared for\nthe session")
  responded_needs <- plot_data |> TeachingLab::agree_strongly_agree(question = "They responded to the group’s\nneeds")
  facilitated_clearly <- plot_data |> TeachingLab::agree_strongly_agree(question = "They facilitated the content\nclearly")
  effectively_built <- plot_data |> TeachingLab::agree_strongly_agree(question = "They effectively built a safe\nlearning community")
  demonstrated_knowledge <- plot_data |> TeachingLab::agree_strongly_agree(question = "They demonstrated deep\nknowledge of the content they\nfacilitated")
} else {
  fully_prepared <- "There is no data to show the % that"
  responded_needs <- "There is no data to show the % that"
  facilitated_clearly <- "There is no data to show the % that"
  effectively_built <- "There is no data to show the % that"
  demonstrated_knowledge <- "There is no data to show the % that"
}

plot_data |>
  ggplot(aes(x = Question, y = Percent, fill = Response)) +
  geom_col(position = position_stack(reverse = T)) +
  geom_text(aes(label = ifelse(Percent >= 5, paste0(round(Percent), "%"), "")),
    position = position_stack(reverse = T, vjust = 0.5),
    family = "Calibri Bold",
    fontface = "bold",
    size = 6.5
  ) +
  coord_flip() +
  labs(x = "", y = "", title = "% Responses to Each Question") +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  scale_fill_manual(values = c(
    "(5) Strongly agree" = "#04ABEB",
    "(4) Agree" = "#0182B4", "(3) Neither agree nor disagree" = "#02587A",
    "(2) Disagree" = "#032E3F", "(1) Strongly disagree" = "#040404"
  )) +
  TeachingLab::theme_tl() +
  theme(legend.position = "bottom",
        )
```

</center>

- `r fully_prepared` strongly agree or agree that the facilitators were fully prepared for the session.
- `r responded_needs` strongly agree or agree that the facilitators responded to the group’s needs.
- `r facilitated_clearly` strongly agree or agree that the facilitators facilitated the content clearly.
- `r effectively_built` strongly agree or agree that the facilitators effectively built a safe learning community.
- `r demonstrated_knowledge` strongly agree or agree that the facilitators demonstrated deep knowledge of the content they facilitated.

## Facilitator Qualitative Feedback

### What is one thing from today's learning that you plan to take back to your classroom?

<center>

```{r qualitative-feedback-1}
if (sum(!is.na(final_session_survey_df$`What is one thing from today's learning that you plan to take back to your classroom?`)) >= 1) {
  final_session_survey_df |>
    select(`What is one thing from today's learning that you plan to take back to your classroom?`
    ) |>
    TeachingLab::quote_viz(
      text_col = c(
        "What is one thing from today's learning that you plan to take back to your classroom?"
      ),
      print = F,
      width = 80
    )
} else {
  no_data_plot
}
```

</center>

### What went well in today’s session?

<center>

```{r qualitative-feedback-2}
if (sum(!is.na(final_session_survey_df$`What went well in today’s session?`)) >= 1) {
  final_session_survey_df |>
    select(`What went well in today’s session?`) |>
    TeachingLab::quote_viz(
      text_col = c(
        "What went well in today’s session?"
      ),
      print = F,
      width = 80
    )
} else {
  no_data_plot
}
```

</center>

### What could have been better about today’s session?

<center>

```{r qualitative-feedback-3}
if (sum(!is.na(final_session_survey_df$`What could have been better about today’s session?`)) >= 1) {
  final_session_survey_df |>
    select(`What could have been better about today’s session?`) |>
    TeachingLab::quote_viz(
      text_col = c(
        "What could have been better about today’s session?"
      ),
      print = F,
      width = 80
    )
} else {
  no_data_plot
}
```

</center>

### Additional Feedback

<center>

```{r qualitative-feedback-4}
if (sum(!is.na(final_session_survey_df$additional_feedback)) >= 1) {
  final_session_survey_df |>
    select(`Additional feedback` = additional_feedback) |>
    TeachingLab::quote_viz(
      text_col = c(
        "Additional feedback"
      ),
      print = F,
      width = 80
    )
} else {
  no_data_plot
}
```

</center>
