---
title: "Teaching Lab Report"
output: 
  html_document:
    css: "style.css"
    theme:
      bg: "white"
      fg: "black"
      primary: "#04abeb"
      secondary: "#00DAC6"
      base_font:
        Calibri
      heading_font:
        Montserrat
---

```{r setup, include=FALSE}
if (requireNamespace("thematic")) 
  thematic::thematic_rmd(font = "auto")
library(tidyverse)
library(TeachingLab)
library(stringdist)
knitr::opts_chunk$set(echo = F, warning = F, message = F)
na_df <- c("none", "None", "n/a", "N/A", "N/a", "NA", "na", "none", "none.", "na.", "NA.", "N/A.", "No Response")

df <- read_rds(here::here("data/session_survey_21_22data.rds")) %>%
  mutate(leven = stringdist("north andover", 
                            `Select your site (district, parish, network, or school). - Other (please specify)`,
                            method = "lv")) %>%
  filter(leven < 12) %>%
  slice(c(-1, -26, -27)) %>%
  select(-survey_id, -collector_id, -respondent_id, -date_created, -date_modified, -response_status) %>%
  rename(`How much do you agree with the following statements about this facilitator today? - They responded to the group's needs.` = `How much do you agree with the following statements about this facilitator today? - They responded to the group’s needs.`)

df_split <- df %>%
  group_by(Facilitator) %>%
  group_split()

map(1:length(df_split), ~ assign(df_split[[.x]]$Facilitator[1] %>% str_replace_all(., " ", "_"), 
                                 df_split[[.x]],
                                 envir = .GlobalEnv))
```

## North Andover Facilitator Feedback Overall

```{r fig.width = 14.2, fig.height = 10}
overall <- df %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group's needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )

overall %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", overall %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

- 82% of participants agree or strongly agree that the facilitator was fully prepared for the session.

- 60% of participants agree or strongly agree that the facilitator responded to the group's needs.

- 64% of participants agree or strongly agree that the facilitator facilitated the content clearly.

- 69% of participants agree or strongly agree that the facilitator effectively built a safe learning community.

- 73% of participants agree or strongly agree that the facilitator had deep knowledge of the content they facilitated.

## North Andover Facilitator Feedback Individually

Below I compile participant feedback for all quantifiable questions for each facilitator on the left side of the tab, and qualitative feedback on the right side.

## Facilitator Feedback {.tabset .tabset-pills}

### Alisha Powers

<div class = "row">
<div class = "col-md-6">

#### Quantitative

```{r fig.height = 10, fig.width = 10}
callie_agree <- Alisha_Powers %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group's needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )

callie_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", callie_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

</div>

<div class = "col-md-5">

#### Qualitative

```{r fig.align = "left"}
devtools::load_all()
Alisha_Powers %>%
  select(Facilitation_Feedback, `What went well in today’s session?`, `What could have been better about today’s session?`) %>%
  pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
  drop_na() %>%
  filter(Response %!in% na_df) %>%
  mutate(Question = str_replace_all(Question, "Facilitation_Feedback", "What additional feedback do you have about their facilitation skills?")) %>%
  TeachingLab::quote_viz(., text_col = "Response", extra_cols = "Question", align = "left",
                         title = glue::glue("All Responses for {Alisha_Powers$Facilitator[1]}"),
                         width = 90)
```

</div>
</div>

### Ashmeet Sani

<div class = "row">
<div class = "col-md-6">

#### Quantitative

```{r fig.width = 10, fig.height = 10}
elizabeth_agree <- Ashmeet_Sahni %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group's needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )
elizabeth_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", elizabeth_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

</div>

<div class = "col-md-5">

#### Qualitative

```{r fig.align = "left"}
Ashmeet_Sahni %>%
  select(Facilitation_Feedback, `What went well in today’s session?`, `What could have been better about today’s session?`) %>%
  pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
  drop_na() %>%
  filter(Response %!in% na_df) %>%
  mutate(Question = str_replace_all(Question, "Facilitation_Feedback", "What additional feedback do you have about their facilitation skills?")) %>%
  TeachingLab::quote_viz(., text_col = "Response", extra_cols = "Question", align = "left",
                         title = glue::glue("All Responses for {Ashmeet_Sahni$Facilitator[1]}"),
                         width = 90)
```

</div>
</div>

### Cheryl Fricchione

<div class = "row">
<div class = "col-md-6">

#### Quantitative

```{r fig.width = 10, fig.height = 10}
emily_agree <- Cheryl_Fricchione %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group's needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )
emily_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", emily_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

</div>

<div class = "col-md-5">

#### Qualitative

```{r fig.align = "left"}
Cheryl_Fricchione %>%
  select(Facilitation_Feedback, `What went well in today’s session?`, `What could have been better about today’s session?`) %>%
  pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
  drop_na() %>%
  filter(Response %!in% na_df) %>%
  mutate(Question = str_replace_all(Question, "Facilitation_Feedback", "What additional feedback do you have about their facilitation skills?")) %>%
  TeachingLab::quote_viz(., text_col = "Response", extra_cols = "Question", align = "left",
                         title = glue::glue("All Responses for {Cheryl_Fricchione$Facilitator[1]}"),
                         width = 90)
```

</div>
</div>

### Haley Siegel

<div class = "row">
<div class = "col-md-6">

#### Quantitative

```{r fig.width = 10, fig.height = 10}
evan_agree <- Haley_Siegel %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group's needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )
evan_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", evan_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

</div>

<div class = "col-md-5">

#### Qualitative

```{r fig.align = "left"}
Haley_Siegel %>%
  select(Facilitation_Feedback, `What went well in today’s session?`, `What could have been better about today’s session?`) %>%
  pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
  drop_na() %>%
  filter(Response %!in% na_df) %>%
  mutate(Question = str_replace_all(Question, "Facilitation_Feedback", "What additional feedback do you have about their facilitation skills?")) %>%
  TeachingLab::quote_viz(., text_col = "Response", extra_cols = "Question", align = "left",
                         title = glue::glue("All Responses for {Haley_Siegel$Facilitator[1]}"),
                         width = 90)
```

</div>
</div>

### Kristen Economaki

<div class = "row">
<div class = "col-md-6">

#### Quantitative

```{r fig.width = 10, fig.height = 10}
hanady_agree <- Kristen_Economaki %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group's needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )
hanady_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", hanady_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

</div>

<div class = "col-md-5">

#### Qualitative

```{r fig.align = "left"}
Kristen_Economaki %>%
  select(Facilitation_Feedback, `What went well in today’s session?`, `What could have been better about today’s session?`) %>%
  pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
  drop_na() %>%
  filter(Response %!in% na_df) %>%
  mutate(Question = str_replace_all(Question, "Facilitation_Feedback", "What additional feedback do you have about their facilitation skills?")) %>%
  TeachingLab::quote_viz(., text_col = "Response", extra_cols = "Question", align = "left",
                         title = glue::glue("All Responses for {Kristen_Economaki$Facilitator[1]}"),
                         width = 90)
```

</div>
</div>

### Kristen Taylor

<div class = "row">
<div class = "col-md-6">

#### Quantitative

```{r fig.width = 10, fig.height = 10}
kristen_agree <- Kristen_Taylor %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group's needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )
kristen_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", kristen_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

</div>

<div class = "col-md-5">

#### Qualitative

```{r fig.align = "left"}
Kristen_Taylor %>%
  select(Facilitation_Feedback, `What went well in today’s session?`, `What could have been better about today’s session?`) %>%
  pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
  drop_na() %>%
  filter(Response %!in% na_df) %>%
  mutate(Question = str_replace_all(Question, "Facilitation_Feedback", "What additional feedback do you have about their facilitation skills?")) %>%
  TeachingLab::quote_viz(., text_col = "Response", extra_cols = "Question", align = "left",
                         title = glue::glue("All Responses for {Kristen_Taylor$Facilitator[1]}"),
                         width = 90)
```

</div>
</div>

### Tamala Wiley

<div class = "row">
<div class = "col-md-6">

#### Quantitative

```{r fig.width = 10, fig.height = 10}
mary_agree <- `Tamala_Wiley` %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group's needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )
mary_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", mary_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

</div>

<div class = "col-md-5">

#### Qualitative

```{r fig.align = "left"}
ggplot(data = tibble(x = 0, y = 0, label = "No data here.")) +
  geom_text(aes(x = x, y = y, label = label), size = 15, color = "black") +
  theme_void()
```

</div>
</div>

### NA

<div class = "row">
<div class = "col-md-6">

#### Quantitative

```{r fig.width = 10, fig.height = 10}
megan_agree <- `NA` %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group's needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )
megan_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", megan_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

</div>

<div class = "col-md-5">

#### Qualitative

```{r fig.align = "left"}
ggplot(data = tibble(x = 0, y = 0, label = "No data here.")) +
  geom_text(aes(x = x, y = y, label = label), size = 15, color = "black") +
  theme_void()
```

</div>
</div>

