---
title: "Teaching Lab Report"
output: 
  html_document:
    css: "style.css"
    theme:
      bg: "white"
      fg: "black"
      primary: "#04abeb"
      secondary: "#00DAC6"
      base_font:
        Calibri
      heading_font:
        Montserrat
---

```{r setup, include=FALSE}
if (requireNamespace("thematic")) 
  thematic::thematic_rmd(font = "auto")
library(tidyverse)
library(TeachingLab)
knitr::opts_chunk$set(echo = F, warning = F, message = F)
na_df <- c("none", "None", "n/a", "N/A", "N/a", "NA", "na", "none", "none.", "na.", "NA.", "N/A.", "No Response")
# library(surveymonkey)
# options(sm_oauth_token = "BjVjlV9MiVBgfe1XpS2xPS547c6gkAygKWAgm4Vv539-KbFct5lsqyVGRCZun0GDt21lnJrgn9hDvSjF.KybF58vc.P.jdeKJ8A2UEUHnE2.50e0lp.86EmQmy8-y9tm")
# session_survey <- surveymonkey::fetch_survey_obj(id = 308115193) %>%
#   surveymonkey::parse_survey() %>%
#   dplyr::mutate(date_created = lubridate::date(date_created)) %>%
#   dplyr::mutate(`Select your course.` = dplyr::coalesce(`Select your course.`, `Select your course._2`, `Select your course._3`,
#                                           `Select your course._4`, `Select your course._5`, `Select your course._6`)) %>%
#   dplyr::mutate(Date = lubridate::mdy(`Select the date for this session. - \n    Date / Time\n`)) %>%
#   # Fix this cluttering of names the others result in a bunch of differernt formats
#   dplyr::mutate(dplyr::across(c("Select the name of your facilitator.", "Select the name of your facilitator. - Other (please specify)",
#                   "Select the name of your facilitator._2", "Select the name of your facilitator. - Other (please specify)_2",
#                   "Select the name of your facilitator._3", "Select the name of your facilitator. - Other (please specify)_3"), ~ dplyr::na_if(.x, "Name"))) %>%
#   dplyr::mutate(Facilitator = dplyr::coalesce(`Select the name of your facilitator.`,
#                                 `Select the name of your facilitator._2`,
#                                 `Select the name of your facilitator._3`,
#                                 `Select the name of your facilitator. - Other (please specify)_2`,
#                                 `Select the name of your facilitator. - Other (please specify)_3`),
#          Facilitation_Feedback = dplyr::coalesce(`What additional feedback do you have about their facilitation skills?`,
#                                           `What additional feedback do you have about their facilitation skills?_2`,
#                                           `What additional feedback do you have about their facilitation skills?_3`)) %>%
# dplyr::mutate(`How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.` =
#          dplyr::coalesce(`How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.`,
#                   `How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated._2`,
#                   `How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated._3`)) %>%
# dplyr::mutate(`How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.` =
#          dplyr::coalesce(`How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.`,
#                   `How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly._2`,
#                   `How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly._3`)) %>%
# dplyr::mutate(`How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.` =
#          dplyr::coalesce(`How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.`,
#                   `How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community._2`,
#                   `How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community._3`)) %>%
# dplyr::mutate(`How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.` =
#          dplyr::coalesce(`How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.`,
#                   `How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session._2`,
#                   `How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session._3`)) %>%
# dplyr::mutate(`How much do you agree with the following statements about this facilitator today? - They responded to the group’s needs.` =
#          dplyr::coalesce(`How much do you agree with the following statements about this facilitator today? - They responded to the group’s needs.`,
#                   `How much do you agree with the following statements about this facilitator today? - They responded to the group’s needs._2`,
#                   `How much do you agree with the following statements about this facilitator today? - They responded to the group’s needs._3`))
# 
# filtered <- session_survey %>%
#   dplyr::filter(`Select your site (district, parish, network, or school).` == "San Diego Unified School District, CA") #%>%
  # dplyr::filter(Date >= as.Date("2021-10-05"))

# write_rds(filtered, here::here("Data-Clean/surveymonkey_session_sandiego2.rds"))

df <- read_rds(here::here("Data-Clean/surveymonkey_session_sandiego2.rds")) %>%
  select(-survey_id, -collector_id, -respondent_id, -date_created, -date_modified, -response_status) %>%
  rename(`How much do you agree with the following statements about this facilitator today? - They responded to the group's needs.` = `How much do you agree with the following statements about this facilitator today? - They responded to the group’s needs.`)

df_split <- df %>%
  group_by(Facilitator) %>%
  group_split()

map(1:length(df_split), ~ assign(df_split[[.x]]$Facilitator[1] %>% str_replace_all(., " ", "_"), 
                                 df_split[[.x]],
                                 envir = .GlobalEnv))

course_survey <- read_rds(here::here("data/course_surveymonkey.rds")) %>%
  filter(`Select your site (district, parish, network, or school).` == "San Diego Unified School District")
```

## San Diego Participant Feedback

```{r include = F}
nps <- course_survey$`On a scale of 0-10, how likely are you to recommend this course to a colleague or friend? - ` %>%
  str_replace_all(., "10 - Extremely likely", "10") %>%
  str_replace_all(., "5 - Neither likely nor unlikely", "5") %>%
  str_replace_all(., "0 - Not likely at all", "0") %>%
  as.numeric() %>%
  purrr::keep( ~ !is.na(.x)) %>%
  calc_nps()

percent_above_seven <- course_survey %>%
  drop_na(`On a scale of 0-10, how likely are you to recommend this course to a colleague or friend? - `) %>%
  mutate(seven = if_else(`On a scale of 0-10, how likely are you to recommend this course to a colleague or friend? - ` >= 7,
                         T,
                         F)) %>%
  summarise(yes = sum(seven, na.rm = T), all = length(seven)) %>%
  summarise(yes/all*100) %>%
  round() %>%
  as_vector() %>%
  paste0(.,"%")
```


On a scale of 1-10, `r colorize("62%", "#04abeb")` of participants rated the course a 7 or higher.

<!-- , and there was an overall nps of `r colorize(12, "#04abeb")`. -->

```{r fig.width = 15, fig.height = 10}
course_agree <- course_survey %>%
  rename_with( ~ str_replace_all(., "’", "'")) %>%
  select(c(
          "How much do you agree with the following statements about this course? - I am satisfied with the overall quality of this course.",
          "How much do you agree with the following statements about this course? - I am satisfied with how the course was facilitated.",
          "How much do you agree with the following statements about this course? - The independent online work activities were well-designed to help me meet the learning targets.",
          "How much do you agree with the following statements about this course? - I felt a sense of community with the other participants in this course. even though we were meeting virtually.",
          "How much do you agree with the following statements about this course? - The strategies I've learned in this course will improve my instruction.",
          "How much do you agree with the following statements about this course? - The strategies I've learned in this course will improve my coaching or supervision of teachers.",
          "How much do you agree with the following statements about this course? - The strategies I've learned in the course are easy to implement.",
          "How much do you agree with the following statements about this course? - I will apply what I have learned in this course to my practice in the next 4-6 weeks.",
          "How much do you agree with the following statements about this course? - This course has supported me in being responsive to students' backgrounds, cultures, and points of view."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this course\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )
course_agree %>%
  ggplot(aes(x = fct_reorder(Question, Percent, .desc = T), y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Likert Scales of Agreement with the Following Statements",
          x = "", y = ""
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.y = element_text(lineheight = 1.1, size = 12),
          # axis.text.x = element_text(size = 11),
          axis.text.x = element_blank(),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1),
          legend.key.size = unit(1.25, "cm")
        )
```


Below is interactive participant feedback for facilitators. Quantitative results are on the left and qualitative results are on the right.

## Facilitator Feedback {.tabset .tabset-pills}

### Adelfa Hegarty

<div class = "row">
<div class = "col-md-6">

#### Quantitative

```{r fig.height = 10, fig.width = 10}
adelfa_agree <- Adelfa_Hegarty %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group's needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )

adelfa_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", adelfa_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

</div>

<div class = "col-md-5">

#### Qualitative

```{r fig.align = "left"}
devtools::load_all()
Adelfa_Hegarty %>%
  select(Facilitation_Feedback, `What went well in today’s session?`, `What could have been better about today’s session?`) %>%
  pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
  drop_na() %>%
  filter(Response %!in% na_df) %>%
  mutate(Question = str_replace_all(Question, "Facilitation_Feedback", "What additional feedback do you have about their facilitation skills?")) %>%
  TeachingLab::quote_viz(., text_col = "Response", extra_cols = "Question", align = "left",
                         title = glue::glue("All Responses for {Adelfa_Hegarty$Facilitator[1]}"),
                         width = 90)
```

</div>
</div>

### Alisha Powers

<div class = "row">
<div class = "col-md-6">

#### Quantitative

```{r fig.width = 10, fig.height = 10}
alisha_agree <- Alisha_Powers %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group's needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )
alisha_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", alisha_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

</div>

<div class = "col-md-5">

#### Qualitative

```{r fig.align = "left"}
Alisha_Powers %>%
  select(Facilitation_Feedback, `What went well in today’s session?`, `What could have been better about today’s session?`) %>%
  pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
  drop_na() %>%
  filter(Response %!in% na_df) %>%
  mutate(Question = str_replace_all(Question, "Facilitation_Feedback", "What additional feedback do you have about their facilitation skills?")) %>%
  TeachingLab::quote_viz(., text_col = "Response", extra_cols = "Question", align = "left",
                         title = glue::glue("All Responses for {Alisha_Powers$Facilitator[1]}"),
                         width = 90)
```

</div>
</div>

### Ashmeet Sahni

<div class = "row">
<div class = "col-md-6">

#### Quantitative

```{r fig.width = 10, fig.height = 10}
ashmeet_agree <- Ashmeet_Sahni %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group's needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )
ashmeet_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", ashmeet_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

</div>

<div class = "col-md-5">

#### Qualitative

```{r fig.align = "left"}
Ashmeet_Sahni %>%
  select(Facilitation_Feedback, `What went well in today’s session?`, `What could have been better about today’s session?`) %>%
  pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
  drop_na() %>%
  filter(Response %!in% na_df) %>%
  mutate(Question = str_replace_all(Question, "Facilitation_Feedback", "What additional feedback do you have about their facilitation skills?")) %>%
  TeachingLab::quote_viz(., text_col = "Response", extra_cols = "Question", align = "left",
                         title = glue::glue("All Responses for {Ashmeet_Sahni$Facilitator[1]}"),
                         width = 90)
```

</div>
</div>

### Bethany Brown

<div class = "row">
<div class = "col-md-6">

#### Quantitative

```{r fig.width = 10, fig.height = 10}
bethany_agree <- Bethany_Brown %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group's needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )
bethany_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", bethany_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

</div>

<div class = "col-md-5">

#### Qualitative

```{r fig.align = "left"}
Bethany_Brown %>%
  select(Facilitation_Feedback, `What went well in today’s session?`, `What could have been better about today’s session?`) %>%
  pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
  drop_na() %>%
  filter(Response %!in% na_df) %>%
  mutate(Question = str_replace_all(Question, "Facilitation_Feedback", "What additional feedback do you have about their facilitation skills?")) %>%
  TeachingLab::quote_viz(., text_col = "Response", extra_cols = "Question", align = "left",
                         title = glue::glue("All Responses for {Bethany_Brown$Facilitator[1]}"),
                         width = 90)
```

</div>
</div>

### Callie Herring

<div class = "row">
<div class = "col-md-6">

#### Quantitative

```{r fig.width = 10, fig.height = 10}
callie_agree <- Callie_Herring %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group's needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )
callie_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", callie_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

</div>

<div class = "col-md-5">

#### Qualitative

```{r fig.align = "left"}
Callie_Herring %>%
  select(Facilitation_Feedback, `What went well in today’s session?`, `What could have been better about today’s session?`) %>%
  pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
  drop_na() %>%
  filter(Response %!in% na_df) %>%
  mutate(Question = str_replace_all(Question, "Facilitation_Feedback", "What additional feedback do you have about their facilitation skills?")) %>%
  TeachingLab::quote_viz(., text_col = "Response", extra_cols = "Question", align = "left",
                         title = glue::glue("All Responses for {Callie_Herring$Facilitator[1]}"),
                         width = 90)
```

</div>
</div>

### Emily Griffin

<div class = "row">
<div class = "col-md-6">

#### Quantitative

```{r fig.width = 10, fig.height = 10}
emily_agree <- Emily_Griffin %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group's needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )
emily_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", emily_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

</div>

<div class = "col-md-5">

#### Qualitative

```{r fig.align = "left"}
Emily_Griffin %>%
  select(Facilitation_Feedback, `What went well in today’s session?`, `What could have been better about today’s session?`) %>%
  pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
  drop_na() %>%
  filter(Response %!in% na_df) %>%
  mutate(Question = str_replace_all(Question, "Facilitation_Feedback", "What additional feedback do you have about their facilitation skills?")) %>%
  TeachingLab::quote_viz(., text_col = "Response", extra_cols = "Question", align = "left",
                         title = glue::glue("All Responses for {Emily_Griffin$Facilitator[1]}"),
                         width = 90)
```

</div>
</div>

### Emily Howard

<div class = "row">
<div class = "col-md-6">

#### Quantitative

```{r fig.width = 10, fig.height = 10}
emily2_agree <- Emily_Howard %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group's needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )
emily2_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", emily2_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

</div>

<div class = "col-md-5">

#### Qualitative

```{r fig.align = "left"}
Emily_Howard %>%
  select(Facilitation_Feedback, `What went well in today’s session?`, `What could have been better about today’s session?`) %>%
  pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
  drop_na() %>%
  filter(Response %!in% na_df) %>%
  mutate(Question = str_replace_all(Question, "Facilitation_Feedback", "What additional feedback do you have about their facilitation skills?")) %>%
  TeachingLab::quote_viz(., text_col = "Response", extra_cols = "Question", align = "left",
                         title = glue::glue("All Responses for {Emily_Howard$Facilitator[1]}"),
                         width = 90)
```

</div>
</div>

### Gregory Leap

<div class = "row">
<div class = "col-md-6">

#### Quantitative

```{r fig.width = 10, fig.height = 10}
gregory_agree <- Gregory_Leap %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group's needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )
gregory_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", gregory_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

</div>

<div class = "col-md-5">

#### Qualitative

```{r fig.align = "left"}
Gregory_Leap %>%
  select(Facilitation_Feedback, `What went well in today’s session?`, `What could have been better about today’s session?`) %>%
  pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
  drop_na() %>%
  filter(Response %!in% na_df) %>%
  mutate(Question = str_replace_all(Question, "Facilitation_Feedback", "What additional feedback do you have about their facilitation skills?")) %>%
  TeachingLab::quote_viz(., text_col = "Response", extra_cols = "Question", align = "left",
                         title = glue::glue("All Responses for {Gregory_Leap$Facilitator[1]}"),
                         width = 90)
```

</div>
</div>

### Hanady Elsayed

<div class = "row">
<div class = "col-md-6">

#### Quantitative

```{r fig.width = 10, fig.height = 10}
hanady_agree <- Hanady_Elsayed %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group's needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )
hanady_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", hanady_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

</div>

<div class = "col-md-5">

#### Qualitative

```{r fig.align = "left"}
Hanady_Elsayed %>%
  select(Facilitation_Feedback, `What went well in today’s session?`, `What could have been better about today’s session?`) %>%
  pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
  drop_na() %>%
  filter(Response %!in% na_df) %>%
  mutate(Question = str_replace_all(Question, "Facilitation_Feedback", "What additional feedback do you have about their facilitation skills?")) %>%
  TeachingLab::quote_viz(., text_col = "Response", extra_cols = "Question", align = "left",
                         title = glue::glue("All Responses for {Hanady_Elsayed$Facilitator[1]}"),
                         width = 90)
```

</div>
</div>

### Kelsey Wasser

<div class = "row">
<div class = "col-md-6">

#### Quantitative

```{r fig.width = 10, fig.height = 10}
kelsey_agree <- Kelsey_Wasser %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group's needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )
kelsey_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", kelsey_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

</div>

<div class = "col-md-5">

#### Qualitative

```{r fig.align = "left"}
Kelsey_Wasser %>%
  select(Facilitation_Feedback, `What went well in today’s session?`, `What could have been better about today’s session?`) %>%
  pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
  drop_na() %>%
  filter(Response %!in% na_df) %>%
  mutate(Question = str_replace_all(Question, "Facilitation_Feedback", "What additional feedback do you have about their facilitation skills?")) %>%
  TeachingLab::quote_viz(., text_col = "Response", extra_cols = "Question", align = "left",
                         title = glue::glue("All Responses for {Kelsey_Wasser$Facilitator[1]}"),
                         width = 90)
```

</div>
</div>

### Kimberly Robertson

<div class = "row">
<div class = "col-md-6">

#### Quantitative

```{r fig.width = 10, fig.height = 10}
kimberly_agree <- Kimberly_Robertson %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group's needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )
kimberly_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", kimberly_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

</div>

<div class = "col-md-5">

#### Qualitative

```{r fig.align = "left"}
Kimberly_Robertson %>%
  select(Facilitation_Feedback, `What went well in today’s session?`, `What could have been better about today’s session?`) %>%
  pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
  drop_na() %>%
  filter(Response %!in% na_df) %>%
  mutate(Question = str_replace_all(Question, "Facilitation_Feedback", "What additional feedback do you have about their facilitation skills?")) %>%
  TeachingLab::quote_viz(., text_col = "Response", extra_cols = "Question", align = "left",
                         title = glue::glue("All Responses for {Kimberly_Robertson$Facilitator[1]}"),
                         width = 90)
```

</div>
</div>

### Kelsey Wasser

<div class = "row">
<div class = "col-md-6">

#### Quantitative

```{r fig.width = 10, fig.height = 10}
kristen_agree <- Kristen_Taylor %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group's needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )
kristen_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", kristen_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

</div>

<div class = "col-md-5">

#### Qualitative

```{r fig.align = "left"}
Kristen_Taylor %>%
  select(Facilitation_Feedback, `What went well in today’s session?`, `What could have been better about today’s session?`) %>%
  pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
  drop_na() %>%
  filter(Response %!in% na_df) %>%
  mutate(Question = str_replace_all(Question, "Facilitation_Feedback", "What additional feedback do you have about their facilitation skills?")) %>%
  TeachingLab::quote_viz(., text_col = "Response", extra_cols = "Question", align = "left",
                         title = glue::glue("All Responses for {Kristen_Taylor$Facilitator[1]}"),
                         width = 90)
```

</div>
</div>

### Mary Shaw-Lewis

<div class = "row">
<div class = "col-md-6">

#### Quantitative

```{r fig.width = 10, fig.height = 10}
mary_agree <- `Mary_Shaw-Lewis` %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group's needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )
mary_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", mary_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

</div>

<div class = "col-md-5">

#### Qualitative

```{r fig.align = "left"}
`Mary_Shaw-Lewis` %>%
  select(Facilitation_Feedback, `What went well in today’s session?`, `What could have been better about today’s session?`) %>%
  pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
  drop_na() %>%
  filter(Response %!in% na_df) %>%
  mutate(Question = str_replace_all(Question, "Facilitation_Feedback", "What additional feedback do you have about their facilitation skills?")) %>%
  TeachingLab::quote_viz(., text_col = "Response", extra_cols = "Question", align = "left",
                         title = glue::glue("All Responses for {`Mary_Shaw-Lewis`$Facilitator[1]}"),
                         width = 90)
```

</div>
</div>

### Sheena Lights

<div class = "row">
<div class = "col-md-6">

#### Quantitative

```{r fig.width = 10, fig.height = 10}
sheena_agree <- Sheena_Lights %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group's needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )
sheena_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", sheena_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

</div>

<div class = "col-md-5">

#### Qualitative

```{r fig.align = "left"}
Sheena_Lights %>%
  select(Facilitation_Feedback, `What went well in today’s session?`, `What could have been better about today’s session?`) %>%
  pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
  drop_na() %>%
  filter(Response %!in% na_df) %>%
  mutate(Question = str_replace_all(Question, "Facilitation_Feedback", "What additional feedback do you have about their facilitation skills?")) %>%
  TeachingLab::quote_viz(., text_col = "Response", extra_cols = "Question", align = "left",
                         title = glue::glue("All Responses for {Sheena_Lights$Facilitator[1]}"),
                         width = 90)
```

</div>
</div>

