---
title: 'Teaching Lab Report'
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  TeachingLab::TLDefault:
    theme: null
    mathjax: null
    css: styles.css
    fontawesome: true
    self_contained: true
    thumbnails: false
    lightbox: true
    gallery: false
    highlight: kate # Also can do tango
    number_sections: false
    includes:
      in_header: header.html
      after_body: footer.html
runtime: shiny
---

```{r echo = F}
library(shiny)
shiny::selectInput(
  inputId = "siteSelect",
  label = "Please choose a site",
  selected = "",
  choices = all_sites <- c(
    "All Sites",
    "AR_Arkansas DOE",
    "CA_San Diego",
    "CA_Silver Giving",
    "CA_West Contra Costa_Murphy ES",
    "CA_West Contra Costa_WCCUSD",
    "DE_DE Department of Education",
    "IL_Chicago Public Schools_Aggregate",
    "IL_Chicago Public Schools_Network 12",
    "IL_Chicago Public Schools_Network 4",
    "IL_Chicago Public Schools_Network 7",
    "IL_Kankakee District 111",
    "LA_Calcasieu Parish",
    "LA_Jefferson Davis Parish",
    # "LA_Pointe Coupee Parish",
    "NM_NM Public Education Department",
    "NY_Amistad Dual Language",
    "NY_Channel View School for Research",
    "NY_D9",
    "NY_D10_10X386",
    "NY_D27",
    "NY_ESMT_IS190",
    "NY_Fannie Lou Hamer",
    "OH_Cleveland Metro School District",
    "TN_McNairy County Schools",
    "TX_Essence Preparatory Public School",
    "TX_RAISE Rice University",
    "US_City Year",
    "US_Digital Nest",
    "US_Open Enrollment",
    "VT_Danville School",
    "VT_Orleans Central Supervisory Union",
    "WI_WI DPI"
  )
)

site_reactive <- reactive({
  input$siteSelect
})

output$title <- renderText({paste0('Teaching Lab End of Year Report: ', site_reactive())})
```


```{r setup, include=FALSE}
na_df <- c("N.A", "N.A.", "n/a", "N/a", "N/A", "N/A", "N/A.", "na", "Na", "NA", "na.", "NA.", "No Response", "none", "None", "NONE", "none.", "None.", "nothing", "Nothing", "NOTHING", "nothing.", "Nothing.", "response", "Response", NA)
library(ggforce)
library(ggfx)
library(ggtext)
library(glue)
library(grid)
library(gt)
library(here)
library(knitr)
library(lubridate)
library(patchwork)
library(png)
library(qualtRics)
library(rmdformats)
library(scales)
library(TeachingLab)
library(tidyverse)
update_data <- FALSE

### Student Survey Read-In ###
student_survey <- reactive({
  TeachingLab::get_student_survey(update = update_data, year = "22_23") |>
    TeachingLab::neg_cond_filter(
      if_not_this = "All Sites",
      filter_this = input$siteSelect,
      dat_filter = site
    ) |>
    mutate(race = if_else(ethnicity == "Yes", "Hispanic/Latino", race))
})

### IPG Forms Read-In ###
ipg_forms <- reactive({
  TeachingLab::get_ipg_forms(update = update_data, year = "22_23") |>
    TeachingLab::neg_cond_filter(
      if_not_this = "All Sites",
      filter_this = input$siteSelect,
      dat_filter = site
    ) |>
    dplyr::filter(site != "MA_DESE") |>
    dplyr::mutate(
      direct_to_ts_obs = as.character(direct_to_ts_obs),
      not_direct_to_ts = as.character(not_direct_to_ts)
    )
})

ipg_forms_direct_to_ts <- reactive({
  ipg_forms() |>
  dplyr::filter(site %in% c(
    "IL_Chicago Public Schools_Network 7",
    "IL_Chicago Public Schools_Network 4",
    "IL_Chicago Public Schools_Network 12",
    "CPS Aggregate",
    "NY_D9",
    "NY_D11",
    "AR_Arkansas DOE"
  ) & !is.na(direct_to_ts_obs))
})

ipg_forms_not_direct_to_ts <- reactive({
  ipg_forms() |>
  dplyr::filter(!site %in% c(
    "IL_Chicago Public Schools_Network 7",
    "IL_Chicago Public Schools_Network 4",
    "IL_Chicago Public Schools_Network 12",
    "CPS Aggregate",
    "NY_D9",
    "NY_D11",
    "AR_Arkansas DOE"
  ) & !is.na(not_direct_to_ts))
})

section_6_eval <- reactive({
  nrow(ipg_forms()) >= 1
})
ipg_count <- reactive({
  nrow(ipg_forms())
})

### Educator Survey Read-In ###
educator_survey <- reactive({
  ed_survey <- TeachingLab::get_diagnostic_survey(update = update_data, year = "22_23") |>
    TeachingLab::neg_cond_filter(
      if_not_this = "All Sites",
      filter_this = input$siteSelect,
      dat_filter = site
    ) |>
    dplyr::filter(site != "MA_DESE")

  if (input$siteSelect != "NM_NM Public Education Department") {
    ed_survey <- ed_survey |>
      select(-c(`ts_crse_after_7/30_5`:`ts_crse_after_7/30_9`))
  }
  
  ed_survey
})

ed_survey_vars <- c(
  "gender",
  "race_1", "race_2", "race_3", "race_4", "race_5",
  "ethnicity",
  "teaching_experience",
  "content_area",
  paste0("grade_level_", 1:17),
  "tl_pl_participation",
  "role",
  "lab_leader"
)
section_1_eval <- reactive({
  purrr::reduce(purrr::map(ed_survey_vars, ~ sum(!is.na(educator_survey()[[.x]]))), `+`) >= 1
})
section_4_eval <- reactive({
  sum(!is.na(educator_survey()$mindsets_ts_1_1)) >= 1
})
section_5_eval <- reactive({
  sum(!is.na(educator_survey()$non_ts_mindsets_1)) >= 1
})

diagnostic_count <- reactive({
  nrow(educator_survey())
})

### Follow-up Educator Survey Read-In ###
followup_educator <- reactive({
  fl_ed <- TeachingLab::get_followup_educator(update = update_data, year = "22_23") |>
    TeachingLab::neg_cond_filter(
      if_not_this = "All Sites",
      filter_this = input$siteSelect,
      dat_filter = site
    ) |>
    dplyr::filter(site != "MA_DESE")

  if (input$siteSelect != "NM_NM Public Education Department") {
    fl_ed <- fl_ed |>
      select(-c(`ts_crse_after_7/30_5`:`ts_crse_after_7/30_9`))
  }
  
  fl_ed
})

followup_count <- reactive({
  nrow(followup_educator())
})

### Knowledge Assessments Read-In ###
knowledge_assessments <- reactive({
  TeachingLab::get_knowledge_assessments(update = update_data, year = "22_23") |>
    TeachingLab::neg_cond_filter(
      if_not_this = "All Sites",
      filter_this = input$siteSelect,
      dat_filter = site
    ) |>
    dplyr::filter(site != "MA_DESE")
})
section_3_eval <- reactive({
  dplyr::if_else(nrow(knowledge_assessments()) >= 1, TRUE, FALSE)
})

pre_know <- reactive({
  nrow(knowledge_assessments() |> dplyr::filter(prepost == "pre"))
})
post_know <- reactive({
  nrow(knowledge_assessments() |> dplyr::filter(prepost == "post"))
})

### End of Session Feedback Read In ###
session_survey <- reactive({
  TeachingLab::get_session_survey(update = update_data, year = "22_23") |>
    TeachingLab::neg_cond_filter(
      if_not_this = "All Sites",
      filter_this = input$siteSelect,
      dat_filter = site
    ) |>
    dplyr::filter(site != "MA_DESE") |>
    mutate(
      race = case_when(
        ethnicity == "Hispanic or Latino" ~ "Hispanic/Latino",
        (!is.na(race_1) & !is.na(race_2)) |
          (!is.na(race_1) & !is.na(race_3)) |
          (!is.na(race_1) & !is.na(race_4)) |
          (!is.na(race_1) & !is.na(race_5)) |
          (!is.na(race_2) & !is.na(race_3)) |
          (!is.na(race_2) & !is.na(race_4)) |
          (!is.na(race_2) & !is.na(race_5)) |
          (!is.na(race_3) & !is.na(race_4)) |
          (!is.na(race_3) & !is.na(race_5)) |
          (!is.na(race_4) & !is.na(race_5)) ~ "More than one race",
        race_1 == "Asian" ~ "Asian",
        race_2 == "Black or African American" ~ "Black or African American",
        race_3 == "Native American or Indian" ~ "Native American or Indian",
        race_5 == "White" ~ "White",
        race_6 == "Prefer not to say" ~ "Other",
        race_7 == "I prefer to self describe" ~ "Other"
      ),
      content_area = if_else(!content_area %in% c("Math", "ELA"), "Other", content_area)
    )
})
section_2a_eval <- reactive({
  nrow(session_survey()) >= 1
})

### End of Course Feedback Read In ###
course_survey <-
  reactive({
    TeachingLab::get_course_survey(update = update_data, year = "22_23") |>
      TeachingLab::neg_cond_filter(
        if_not_this = "All Sites",
        filter_this = input$siteSelect,
        dat_filter = site
      ) |>
      dplyr::filter(site != "MA_DESE") |>
      dplyr::mutate(
        race = dplyr::case_when(
          ethnicity == "Hispanic or Latino" ~ "Hispanic/Latino",
          (!is.na(race_1) & !is.na(race_2)) |
            (!is.na(race_1) & !is.na(race_3)) |
            (!is.na(race_1) & !is.na(race_4)) |
            (!is.na(race_1) & !is.na(race_5)) |
            (!is.na(race_2) & !is.na(race_3)) |
            (!is.na(race_2) & !is.na(race_4)) |
            (!is.na(race_2) & !is.na(race_5)) |
            (!is.na(race_3) & !is.na(race_4)) |
            (!is.na(race_3) & !is.na(race_5)) |
            (!is.na(race_4) & !is.na(race_5)) ~ "More than one race",
          race_1 == "Asian" ~ "Asian",
          race_2 == "Black or African American" ~ "Black or African American",
          race_3 == "Native American or Indian" ~ "Native American or Indian",
          race_5 == "White" ~ "White",
          race_6 == "Prefer not to say" ~ "Other",
          race_7 == "I prefer to self describe" ~ "Other"
        ),
        content_area = dplyr::if_else(!content_area %in% c("Math", "ELA"), "Other", content_area)
      )
  })
section_2b_eval <- reactive({
  nrow(course_survey()) >= 1
})

### Ongoing Coaching Feedback Read In ###
ongoing_coaching <-
  reactive({
    TeachingLab::get_ongoing_coaching(update = update_data, year = "22_23") |>
      TeachingLab::neg_cond_filter(
        if_not_this = "All Sites",
        filter_this = input$siteSelect,
        dat_filter = site
      ) |>
      dplyr::filter(site != "MA_DESE") |>
      dplyr::mutate(
        race = dplyr::case_when(
          ethnicity == "Hispanic or Latino" ~ "Hispanic/Latino",
          (!is.na(race_1) & !is.na(race_2)) |
            (!is.na(race_1) & !is.na(race_3)) |
            (!is.na(race_1) & !is.na(race_4)) |
            (!is.na(race_1) & !is.na(race_5)) |
            (!is.na(race_2) & !is.na(race_3)) |
            (!is.na(race_2) & !is.na(race_4)) |
            (!is.na(race_2) & !is.na(race_5)) |
            (!is.na(race_3) & !is.na(race_4)) |
            (!is.na(race_3) & !is.na(race_5)) |
            (!is.na(race_4) & !is.na(race_5)) ~ "More than one race",
          race_1 == "Asian" ~ "Asian",
          race_2 == "Black or African American" ~ "Black or African American",
          race_3 == "Native American or Indian" ~ "Native American or Indian",
          race_5 == "White" ~ "White",
          race_6 == "Prefer not to say" ~ "Other",
          race_7 == "I prefer to self describe" ~ "Other"
        ),
        content_area = dplyr::if_else(!content_area %in% c("Math", "ELA"), "Other", content_area)
      )
  })
section_2c_eval <- reactive({
  nrow(ongoing_coaching()) >= 1
})

### End of Coaching Feedback Read In ###
end_coaching <-
  reactive({
    TeachingLab::get_end_coaching(update = update_data, year = "22_23") |>
      TeachingLab::neg_cond_filter(
        if_not_this = "All Sites",
        filter_this = input$siteSelect,
        dat_filter = site
      ) |>
      dplyr::filter(site != "MA_DESE") |>
      dplyr::mutate(
        race = dplyr::case_when(
          ethnicity == "Hispanic or Latino" ~ "Hispanic/Latino",
          (!is.na(race_1) & !is.na(race_2)) |
            (!is.na(race_1) & !is.na(race_3)) |
            (!is.na(race_1) & !is.na(race_4)) |
            (!is.na(race_1) & !is.na(race_5)) |
            (!is.na(race_2) & !is.na(race_3)) |
            (!is.na(race_2) & !is.na(race_4)) |
            (!is.na(race_2) & !is.na(race_5)) |
            (!is.na(race_3) & !is.na(race_4)) |
            (!is.na(race_3) & !is.na(race_5)) |
            (!is.na(race_4) & !is.na(race_5)) ~ "More than one race",
          race_1 == "Asian" ~ "Asian",
          race_2 == "Black or African American" ~ "Black or African American",
          race_3 == "Native American or Indian" ~ "Native American or Indian",
          race_5 == "White" ~ "White",
          race_6 == "Prefer not to say" ~ "Other",
          race_7 == "I prefer to self describe" ~ "Other"
        ),
        content_area = dplyr::if_else(!content_area %in% c("Math", "ELA"), "Other", content_area)
      )
  })
section_2d_eval <- reactive({
  nrow(end_coaching()) >= 1
})

### Mid/End Year Contact Lead ###
contact_lead <-
  reactive({
    qualtRics::fetch_survey(
      surveyID = "SV_cTJGFaslXUpKVgi",
      verbose = FALSE,
      include_display_order = FALSE,
      force_request = update_data
    ) |>
      dplyr::filter(Finished == TRUE) |>
      TeachingLab::neg_cond_filter(
        if_not_this = "All Sites",
        filter_this = input$siteSelect,
        dat_filter = site
      ) |>
      dplyr::mutate(
        content_area = dplyr::coalesce(
          content_area_1,
          content_area_2,
          content_area_3
        ),
        content_area = stringr::str_remove_all(content_area, "\\/Literacy")
      ) |>
      dplyr::mutate(dplyr::across(where(is.factor), ~ dplyr::na_if(as.character(.x), "NA")))
  })
section_2e_eval <- reactive({
  nrow(contact_lead()) >= 1
})
section_8_eval <- reactive({
  sum(!is.na(contact_lead()$future_pl_location)) >= 1
})

if (!exists("sw_graded")) {
sw_graded <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/15ixca0QKloZtYLcmj_9Uc20zdQ5FE6pSVj3EBamLoiI/edit?pli=1#gid=0",
      sheet = "Student Work Scores"
    ) |>
      dplyr::mutate(`Grade Band` = stringr::str_replace_all(`Grade Band`, "Other", "K-2")) |>
      dplyr::filter(!is.na(`Submitted By`)) |>
      dplyr::filter(Site != "MA_DESE")
}

### Student Work Grades ###
student_work_grades <-
  reactive({
    sw_graded <- sw_graded |>
      TeachingLab::neg_cond_filter(
        if_not_this = "All Sites",
        filter_this = input$siteSelect,
        dat_filter = Site
      )

    if (input$siteSelect == "IL_Chicago Public Schools_Aggregate") {
      sw_graded <- sw_graded |>
        dplyr::filter(Site != "IL_Chicago Public Schools_Network 4")
    }
    sw_graded
  })

section_7_eval <- reactive({
  nrow(student_survey()) >= 1 | nrow(student_work_grades()) >= 1
})

student_work_count <- reactive({
  student_work_grades() |>
  dplyr::filter((Legible == "New Version" | Legible == "Yes") & !is.null(`Submitted Grade/s`)) |>
  dplyr::select(`Submitted Grade/s`, `Student Work File`) |>
  tidyr::drop_na(`Submitted Grade/s`) |>
  dplyr::mutate(`Submitted Grade/s` = as.character(`Submitted Grade/s`)) |>
  tidyr::separate_rows(`Submitted Grade/s`, sep = ", ") |>
  nrow()
})

###################################################################################################

## Global options
options(max.print = "75", width = 1000)
opts_chunk$set(
  echo = FALSE,
  cache = FALSE,
  prompt = FALSE,
  tidy = TRUE,
  comment = NA,
  message = FALSE,
  warning = FALSE,
  out.extra = 'class="plot"'
)
```

```{=html}
<script src="js/hideOutput.js"></script>
```

### Background

Teaching Lab collects a variety of data to understand the impact of its
PL for educators and students. Please see this
[resource](https://docs.google.com/presentation/d/1Vo844M0_Au8bqfeK5-hPdFh30oGRjzjCxwm6vctemQ8/edit#slide=id.g1165a219667_0_182)
for a visual overview of our evaluation framework. Additionally, the
[narrative](https://docs.google.com/document/d/19yDyFCx1KeSPHlD9SLvLfG76FRGdfChL1hnCo_dV1zQ/edit)
of our evaluation plan provides more details.

To date (`r Sys.Date() |> format("%b %d, %Y")`), Teaching Lab has
collected the following data during SY22-23:

```{r session-survey-collection, results = 'asis'}
final_sec_intro <- reactive({
  counts <- list()
  if (nrow(session_survey()) >= 1) {
    sec2_intro <- "Participant Perceptions"
    counts$p1 <- paste0("- ", format(nrow(session_survey()), big.mark = ","), " complete responses to the End of Session Survey section of the survey that gathers participant feedback on facilitation from session to session;")
  }
  if (nrow(course_survey()) >= 1) {
    sec2_intro <- "Participant Perceptions"
    counts$p2 <- paste0("- ", format(nrow(course_survey()), big.mark = ","), " complete responses to the End of Course Survey section of the survey that gathers participant feedback on each PL course;")
  }
  if (nrow(ongoing_coaching()) >= 1) {
    sec2_intro <- "Participant Perceptions"
    counts$p3 <- paste0("- ", format(nrow(ongoing_coaching()), big.mark = ","), " complete responses to the Ongoing Coaching section of the survey that gathers participant feedback on each Coaching session;\n")
  }
  if (nrow(end_coaching()) >= 1) {
    sec2_intro <- "Participant Perceptions"
    counts$p4 <- paste0("- ", format(nrow(end_coaching()), big.mark = ","), " complete responses to the End of Coaching section of the survey that gathers participant feedback on each Coaching performance;")
  }
  if (sum(nrow(session_survey()), nrow(course_survey()), nrow(ongoing_coaching()), nrow(end_coaching())) == 0) {
    sec2_intro <- NA
  }
  if (pre_know() >= 1) {
    sec3_intro <- "Participant Knowledge"
    counts$p5 <- paste0("- ", pre_know(), " complete responses to the first Knowledge or Self-Reported Practices Assessments and ", post_know(), " to the second Knowledge or Self-Reported Practices Assessments;")
  } else {
    sec3_intro <- NA
  }
  if (diagnostic_count() >= 1) {
    sec1_intro <- "Participant Background and Demographics Summary"
    sec4_intro <- "Teachers' Mindsets & School Environment"
    sec5_intro <- "School Leaders' Mindsets & Observational Practices"
    counts$p6 <- paste0("- ", format(diagnostic_count(), big.mark = ","), " complete responses to the Baseline Diagnostic Educator Survey that collects information on teachers' use of curricula, mindsets, self-reported practices, and school environment & ", format(followup_count(), big.mark = ","), " responses to the Follow-up Educator Survey.")
  } else {
    sec1_intro <- NA
    sec4_intro <- NA
    sec5_intro <- NA
  }
  if (ipg_count() >= 1) {
    sec6_intro <- "Instructional Practice"
    counts$p7 <- paste0("- ", format(ipg_count(), big.mark = ","), " observations of classroom instruction.")
  } else {
    sec6_intro <- NA
  }
  if (student_work_count() >= 1) {
    sec7_intro <- "Student Outcomes"
    counts$p8 <- paste0("- ", format(student_work_count(), big.mark = ","), " high quality samples of student work.")
  } else {
    sec7_intro <- NA
  }
  if (sum(!is.na(contact_lead()$future_pl_location))) {
    sec8_intro <- "Partnership Opportunities Moving Forward"
  } else {
    sec8_intro <- NA
  }
  
  inline_sections <- na.omit(c(
    sec1_intro,
    sec2_intro,
    sec3_intro,
    sec4_intro,
    sec5_intro,
    sec6_intro,
    sec7_intro,
    sec8_intro
  ))
  final_sec_intro <- glue::glue_collapse(inline_sections, ", ", last = " and ")
  
  list(counts = counts, final_sec_intro = final_sec_intro)
})
e
output$counts <- renderUI({
  # counts <- final_sec_intro()[grep('p', names(final_sec_intro()))]
  final_counts <- final_sec_intro()$counts
  test <- purrr::map_chr(1:length(final_counts), ~ final_counts[[.x]])
  HTML(paste(test, collapse = "</br>"))
})

output$final_sec_intro <- renderText({
  final_sec_intro()$final_sec_intro
})
```

`r htmlOutput("counts")`

Below we have compiled the results in various sections:

`r textOutput("final_sec_intro")`.

```{r section-1, results = 'asis'}
# output$section1 <- renderUI({
#   if (section_1_eval() == TRUE) {
#   HTML(paste0("# Section 1: Participant Background and Demographics Summary",
#   "<br/>",
#   "This section provides a demographic and background summary on participants."))
#   } else {
#     ""
#   }
# })
# 
# htmlOutput("section1")
```

# Section 1: Participant Background and Demographics Summary

This section provides a demographic and background summary on participants.

## Gender and Racial Identity


```{r section-1-gts, fig.dim = c(6.5, 4.5), fig.align = 'center', results = 'asis'}
output$gender_plot <- renderPlot({
  gender_plot <- TeachingLab::gt_percent_n(
    df = educator_survey(),
    column = "gender",
    custom_column_name = "Gender Identity", 
    viz_type = sample(c("waffle", "pie", "treemap"), size = 1)
  )
  gender_plot
})

plotOutput("gender_plot")
```

## Racial Identity

```{r section-2-gts, fig.dim = c(6.5, 4.5), fig.align = 'center', results = 'asis'}
race_cols <- c("race_1", "race_2", "race_3", "race_4", "race_5", "race_6", "race_7")

output$race_plot <- renderPlot({
  race_plot <- educator_survey() |>
    select(
      all_of(
        race_cols
      )
    ) |>
    pivot_longer(everything()) |>
    mutate(value = fct_lump(factor(value), 3)) |>
    rename(`Race Identity` = value) |>
    gt_percent_n(
      column = "Race Identity",
      custom_column_name = "Racial Identity",
      viz_type = sample(c("pie", "waffle", "treemap"), size = 1)
    )
  race_plot
})

plotOutput("race_plot")
```


```{r section-3-gts, fig.dim = c(6.5, 4.5), fig.align = 'center', results = 'asis'}
# render_gt({
# if (sum(!is.na(educator_survey()$ethnicity)) >= 1) {
#   ethnicity_gt <- gt_percent_n(
#     educator_survey()[!str_detect(educator_survey()$ethnicity, "NA"), ],
#     column = "ethnicity",
#     custom_column_name = "Ethnicity", viz_type = sample(c("pie", "waffle", "treemap"),
#       size = 1
#     )
#   )
# 
#   print(ethnicity_gt)
# 
#   cat("\n")
# }
# })
# 
# renderPlot({
# if (sum(!is.na(educator_survey()$teaching_experience)) >= 1) {
#   n <- sum(!is.na(educator_survey()$teaching_experience[!str_detect(educator_survey()$teaching_experience, "NA")]))
# 
#   teaching_experience_plot <- educator_survey() |>
#     drop_na(teaching_experience) |>
#     dplyr::filter(!str_detect(teaching_experience, "NA")) |>
#     dplyr::mutate(teaching_experience = na.omit(teaching_experience)) |>
#     group_by(teaching_experience) |>
#     count(sort = T) |>
#     ungroup() |>
#     mutate(
#       percent = round(100 * n / sum(n), 1),
#       color = if_else(percent < 10, "black", "white"),
#       hjust = if_else(color == "white", 1.5, -0.5)
#     ) |>
#     ggplot(aes(teaching_experience, percent)) +
#     geom_col(aes(fill = percent)) +
#     geom_text(
#       aes(
#         label = paste0(percent, "%"),
#         color = color, hjust = hjust
#       ),
#       fontface = "bold"
#     ) +
#     coord_flip() +
#     labs(title = glue::glue("Years of Teaching Experience (n = {format(n, big.mark = ',')})"), x = "", y = "") +
#     scale_color_manual(values = c("black", "white")) +
#     scale_fill_continuous() +
#     scale_y_continuous(
#       labels = scales::percent_format(scale = 1),
#       breaks = scales::pretty_breaks(n = 6)
#     ) +
#     scale_x_discrete(labels = c("Less than 1", "0-9", "10-19", "20-29", "30-39", "40-49", "50+")) +
#     ggplot2::theme(
#       axis.text = ggtext::element_markdown(size = 20),
#       axis.title = ggtext::element_markdown(size = 24)
#     ) +
#     TeachingLab::theme_tl()
# 
#   cat("\n## Years of Teaching Experience", "\n")
# 
#   print(teaching_experience_plot)
# 
#   cat("\n")
# }
# })
# 
# render_gt({
# if (sum(!is.na(educator_survey()$content_area)) >= 1 & input$siteSelect != "US_Digital Nest") {
#   content_area_gt <- educator_survey() |>
#     select(content_area) |>
#     drop_na() |>
#     dplyr::filter(!str_detect(content_area, "NA")) |>
#     gt_percent_n(
#       column = "content_area",
#       custom_column_name = "Content Area", viz_type = sample(c("waffle", "pie", "treemap"),
#         size = 1
#       )
#     )
# 
#   cat("\n## Content Area", "\n")
# 
#   print(content_area_gt)
# 
#   cat("\n")
# }
# })
# 
# renderPlot({
# grades <- c(map_chr(1:14, ~ paste0("grade_level_", .x)))
# if (reduce(map(grades, ~ sum(!is.na(educator_survey()[[.x]]))), `+`) >= 1) {
#   n <- educator_survey() |>
#     select(all_of(grades)) |>
#     janitor::remove_empty("rows") |>
#     nrow()
# 
#   grades_plot <- educator_survey() |>
#     select(all_of(grades)) |>
#     mutate(across(everything(), ~ as.character(.x))) |>
#     pivot_longer(everything()) |>
#     tidyr::drop_na(value) |>
#     group_by(value) |>
#     count(sort = T) |>
#     ungroup() |>
#     mutate(
#       percent = round(100 * n / sum(n), 1),
#       value = factor(value, levels = c(
#         "K", "1", "2", "3", "4", "5",
#         "6", "7", "8", "9", "10", "11",
#         "12", "Other"
#       ))
#     ) |>
#     ggplot(aes(value, percent)) +
#     geom_col(aes(fill = percent)) +
#     geom_text(
#       aes(
#         label = paste0(percent, "%"),
#         vjust = -0.5
#       ),
#       fontface = "bold"
#     ) +
#     labs(
#       y = "", x = "Grade",
#       title = glue::glue("Grades Taught (n = {format(n, big.mark = ',')})"),
#       subtitle = "<i>More than one could be selected.</i>"
#     ) +
#     scale_color_manual(values = c("black", "white")) +
#     scale_fill_continuous() +
#     scale_y_continuous(
#       labels = scales::percent_format(scale = 1),
#       breaks = scales::pretty_breaks(n = 6)
#     ) +
#     theme_tl() +
#     theme(
#       axis.text = element_markdown(size = 20),
#       axis.title = element_markdown(size = 24),
#       plot.subtitle = element_markdown()
#     )
# 
#   cat("\n## Grades", "\n")
# 
#   print(grades_plot)
# 
#   cat("\n")
# }
# })
# 
# render_gt({
# if (sum(!str_detect(educator_survey()$tl_pl_participation, "NA"), na.rm = T) >= 1) {
#   tl_pl_gt <- gt_percent_n(
#     df = educator_survey()[!str_detect(educator_survey()$tl_pl_participation, "NA"), ],
#     column = "tl_pl_participation",
#     custom_column_name = "Previous Experience with Teaching Lab", viz_type = sample(c("waffle", "pie", "treemap"),
#       size = 1
#     )
#   )
# 
#   cat("\n## Prior Experience with Teaching Lab Professional Learning", "\n")
# 
#   print(tl_pl_gt)
# 
#   cat("\n")
# }
# })
# 
# render_gt({
# if (sum(!str_detect(educator_survey()$role, "NA"), na.rm = T) >= 1) {
#   roles_gt <- gt_percent_n(
#     df = educator_survey()[!str_detect(educator_survey()$role, "NA"), ],
#     column = "role",
#     custom_column_name = "Primary Role",
#     viz_type = sample(c("waffle", "treemap"),
#       size = 1
#     )
#   )
# 
#   cat("\n## Roles", "\n")
# 
#   print(roles_gt)
# 
#   cat("\n")
# }
# })
# 
# render_gt({
# if (sum(!str_detect(educator_survey()$lab_leader, "NA"), na.rm = T) >= 1) {
#   lab_leader_gt <- gt_percent_n(
#     df = educator_survey()[!str_detect(educator_survey()$lab_leader, "NA"), ],
#     column = "lab_leader",
#     custom_column_name = "Lab Leader",
#     viz_type = sample(c("waffle", "pie", "treemap"),
#       size = 1
#     )
#   )
# 
#   print(lab_leader_gt)
# 
#   cat("\n")
# }
# })
```
