---
title: "Teaching Lab Report"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  TeachingLab::TLDefault:
    highlight: kate
---

```{r setup, include=FALSE}
library(googledrive)
library(googlesheets4)
library(gt)
library(qualtRics)
library(TeachingLab)
library(tidyverse)

participant_feedback <- fetch_survey(
  surveyID = "SV_djt8w6zgigaNq0C",
  verbose = TRUE,
  force_request = TRUE
) |>
  dplyr::filter(Finished == TRUE)

## Global options
opts_chunk$set(
  echo = FALSE,
  cache = TRUE,
  prompt = FALSE,
  tidy = TRUE,
  comment = NA,
  message = FALSE,
  warning = FALSE
)
opts_knit$set(width = 75)
```

## Qualtrics Data & Formats 2022-2023

In 2022-2023 Teaching Lab's Learning & Research (L&R) data formats were standardized in both survey creation and API requests via Qualtrics' labeling feature to streamline interfacing with the web survey and pulling data into other platforms. Column naming (labeling in Qualtrics) now follows the formats below for ALL surveys:

-   **Introduction**

    -   Initials - The three letter initials of the survey-taker (X if they do not have or do not want to provide the middle initial) [user text entry]

    -   DOB - The mmyy format of the survey-taker's date of birth [user text entry]

-   **Site Selection**

    -   Site - Site [user dropdown selection]

    -   District 9 - District 9 school [user dropdown selection]

        -   D9_other school - District 9 school if not listed [user text entry]

    -   District 11 - District 11 school [user dropdown selection]

        -   D11_other school - District 11 school if not listed [user text entry]

    -   District 27 - District 27 school [user list selection]

    -   Network 4 - Network 4 school [user list selection]

    -   Network 7 - Network 7 school [user list selection]

    -   Network 12 - Network 12 school [user list selection]

    -   Rochester - Rochester school [user list selection]

    Other naming conventions are subsequently named in their relevant section, such as the Participant Feedback survey, Educator survey, Classroom Observations survey, or Knowledge Assessments surveys.

Finally I display the database schema of all Teaching Lab data moving forward as of `r format(Sys.Date(), "%b %d, %Y")` is established below. Historical data has been standardized into this database, and all future data formats should follow this for the sake of consistency as well. Using this database schema you can subsequently determine what data to query in individual surveys.

```{r}
database_schema <- tibble::tibble(
  participant_id = c("dag0414", "sxw0315", "hmv0320"),
  site = c("Site X", "Site Y", "Site Z"),
  participant_feedback = c(TRUE, TRUE, FALSE),
  educator_survey = c(TRUE, TRUE, TRUE),
  classroom_obs = c(TRUE, FALSE, TRUE),
  knowledge_assess = c(TRUE, FALSE, FALSE),
  year = factor(c("22-23", "22-23", "21-22"), levels = c("22-23", "21-22"))
) |>
  dplyr::arrange(year)

database_schema |>
  gt::gt() |>
  TeachingLab::gt_theme_tl()
```

## Participant Feedback Survey Codebook

The participant feedback database table is structured as so:

```{r}
database_schema_pf <- participant_feedback |>
  select(
    RecordedDate,
    last_session_or_not,
    initials,
    dob,
    selected_date,
    site,
    `District 9`,
    `District 11`,
    `District 27`,
    `Network 4`,
    `Network 7`,
    `Network 12`,
    Rochester,
    role,
    gender,
    race_1,
    race_2,
    race_3,
    race_4,
    race_5,
    race_6,
    race_7,
    ethnicity,
    grade_level_16,
    grade_level_1,
    grade_level_4,
    grade_level_5,
    grade_level_6,
    grade_level_7,
    grade_level_8,
    grade_level_9,
    grade_level_10,
    grade_level_11,
    grade_level_12,
    grade_level_13,
    grade_level_14,
    grade_level_15,
    grade_level_17,
    content_area,
    course,
    location,
    coach,
    coach_other,
    `coach_ongoing_feed_1`,
    `coach_ongoing_feed_2`,
    `coach_ongoing_feed_3`,
    `coach_ongoing_feed_4`,
    `coach_ongoing_feed_5`,
    `coach_additonal_feed`,
    `coach_gone_well`,
    `been_better_coach`,
    facilitator1,
    facilitator_other1,
    fac_feedback_1,
    fac_feedback_2,
    fac_feedback_3,
    fac_feedback_4,
    fac_feedback_5,
    fac_add1,
    second_fac_q,
    facilitator2,
    facilitator_other2,
    fac_feedback_2_1,
    fac_feedback_2_2,
    fac_feedback_2_3,
    fac_feedback_2_4,
    fac_feedback_2_5,
    fac_add_2,
    went_well_today,
    take_back_class,
    been_better_today,
    course_feedback_1,
    course_feedback_2,
    course_feedback_3,
    course_feedback_4,
    course_feedback_5,
    course_feedback_6,
    course_feedback_7,
    course_feedback_8,
    course_feedback_9,
    course_feedback_10,
    course_feedback_11,
    course_feedback_12,
    course_feedback_13,
    course_feedback_14,
    course_feedback_15,
    nps,
    overall_went_well,
    been_better_course,
    learning_excited_try,
    best_activities,
    course_add_comments,
    coach_end_feed_1,
    coach_end_feed_2,
    coach_end_feed_3,
    coach_end_feed_4,
    coach_end_feed_5,
    coach_end_feed_6,
    coach_end_feed_7,
    coach_end_feed_8,
    coach_end_feed_9,
    coach_end_feed_10,
    coach_end_feed_11,
    coach_nps,
    coach_learn_excited,
    coach_activities_sup,
    coach_went_well,
    coach_been_better,
    coach_add_comment
  ) |>
  slice_sample(n = 10)

database_schema_pf |>
  gt::gt() |>
  TeachingLab::gt_theme_tl()
```


## Educator Survey Codebook

The educator survey database table is structured as so:

```{r}
database_schema_es <- educator_survey |>
  select(
    RecordedDate,
    initials,
    dob,
    site,
    `District 9`,
    `District 11`,
    `District 27`,
    `Network 4`,
    `Network 7`,
    `Network 12`,
    Rochester,
    role,
    gender,
    race_1,
    race_2,
    race_3,
    race_4,
    race_5,
    race_6,
    race_7,
    ethnicity,
    role,
    content_area,
    grade_level_1,
    grade_level_4,
    grade_level_5,
    grade_level_6,
    grade_level_7,
    grade_level_8,
    grade_level_9,
    grade_level_10,
    grade_level_11,
    grade_level_12,
    grade_level_13,
    grade_level_14,
    teaching_experience,
    tl_pl_participation,
    LL
    ##### Start Recode from here ####
  ) |>
  slice_sample(n = 10)

database_schema_es |>
  gt::gt() |>
  TeachingLab::gt_theme_tl()
```

## Classroom Observations Survey Codebook

The classroom observations database table is structured as so:

```{r}
database_schema_co <- tibble::tibble(
  example = 1
)

database_schema_co |>
  gt::gt() |>
  TeachingLab::gt_theme_tl()
```

## Knowledge Assessments Surveys Codebook

The knowledge assessments database table is structured as so:

```{r}
database_schema_ka <- tibble::tibble(
  example = 1
)

database_schema_ka |>
  gt::gt() |>
  TeachingLab::gt_theme_tl()
```

## Survey Monkey Data & Formats 2021-2022

Below I document my process for cleaning Survey Monkey data from SY21-22 and transferring it to the database for future use.

## Google Sheets and Forms Data & Formats Pre-2021

Below I document my process for processing all remaining data from google drive, sheets, and otherwise.

```{r}
sm_21_22_pf <- TeachingLab::get_session_survey() |>
  bind_cols(TeachingLab::get_course_survey())

database_schema_pf |> colnames()
```
