---
title: "Teaching Lab Annual Goals Progress Monitoring"
subtitle: "FY23 Quarter One: July 1st - September 30th 2022"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  TeachingLab::TLDefault:
    css: styles.css
    fontawesome: false
    self_contained: true
    thumbnails: false
    lightbox: true
    gallery: false
    highlight: kate # Also can do tango
    number_sections: false
    includes:
      in_header: header.html
      after_body: footer.html
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
library(gganimate)
library(ggforce)
library(ggtext)
library(glue)
library(gt)
library(here)
library(knitr)
library(lubridate)
library(patchwork)
library(rmdformats)
library(scales)
devtools::load_all()
library(TeachingLab)
library(tidyverse)

### IPG Forms Read-In ###


###################################################################################################

no_data_plot <- ggplot(tibble(text = "No data here - yet!", x = 0, y = 0)) +
  geom_text(aes(label = text, x, y), fontface = "bold", family = "Calibri Bold", size = 10) +
  theme_void()

# theme_final_report <- function() {
#   theme_tl(legend = T) +
#     theme(
#       axis.text.x = element_blank(),
#       axis.text.y = element_text(
#         lineheight = 0.9, size = 12,
#         margin = margin(t = 0, l = 0, r = -25, b = 0)
#       ),
#       strip.text = element_text(
#         size = 14, face = "bold", family = "Calibri Bold",
#         hjust = 0.5
#       ),
#       panel.grid.major = element_blank(),
#       panel.grid.minor = element_blank(),
#       legend.position = "bottom",
#       legend.margin = margin(-30, 0, 0, 0),
#       legend.key.height = unit(1.3, "cm"),
#       legend.key.width = unit(1.3, "cm"),
#       legend.key.size = unit(0.75, "cm"),
#       legend.text = element_text(size = 11),
#       plot.title = element_text(lineheight = 1.1, size = 18, face = "bold"),
#       plot.subtitle = element_text(size = 14, face = "bold")
#     )
# }

improvement_plot <- function(y_axis_title = "", plot_title = "", pre = 50, post = 60,
                             lim1 = 25, lim2 = 75) {
  data <- tibble::tibble(
    site = c(
      rep(y_axis_title, 2)
    ),
    prepost = c("Pre", "Post"),
    percent = c(pre, post),
  ) |>
    mutate(color = ifelse(prepost == "Pre",
      "#040404",
      "#04ABEB"
    ))

  data_pivot <- data |>
    pivot_wider(!color, names_from = "prepost", values_from = "percent") |>
    mutate(color = "#04abeb")

  data |>
    ggplot(aes(x = percent, y = factor(site), color = prepost)) +
    geom_text(aes(label = paste0(percent, "%")),
      color = data$color,
      nudge_y = 0.15,
      size = 5
    ) +
    ggforce::geom_link(
      data = data_pivot,
      aes(
        x = Pre + 0.1, xend = Post - 0.15, y = site, yend = site,
        color = color, alpha = stat(index) / 2, size = stat(index)
      ),
      color = "#04abeb",
      lineend = "round",
      show.legend = F
    ) +
    geom_point(color = data$color, size = 5) +
    labs(title = plot_title) +
    scale_x_continuous(labels = scales::percent_format(scale = 1), limits = c(lim1, lim2)) +
    scale_y_discrete() +
    TeachingLab::theme_tl() +
    theme(
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      axis.text.y = element_text(size = 18),
      legend.position = "bottom"
    )
}

na_df <- TeachingLab::na_df

## Global options
options(max.print = "75", width = 1000)
opts_chunk$set(
  echo = FALSE,
  cache = FALSE,
  prompt = FALSE,
  tidy = TRUE,
  comment = NA,
  message = FALSE,
  warning = FALSE
)
```

```{=html}
<script src="js/hideOutput.js"></script>
```
### Why:

At Teaching Lab, we set annual organizational goals to ensure we're
strategically and effectively pursuing our mission to fundamentally
shift the paradigm of professional learning for educational equity. Our
organizational goals are a statement of our priorities and our values,
so it's important that, as a team, we keep them close to our hearts and
our work. It's also important that we hold ourselves accountable for
making progress toward them or adjusting course if our progress has
stalled. To that end, with the help of leaders across our organization,
we collect data quarterly about our progress toward our annual
organizational goals. In a spirit of transparency and good stewardship,
we commit to sharing the state of our progress regularly with our
Teaching Lab community and with the stakeholders and communities with
whom we collaborate in the work of educational justice.

### What:

At Teaching Lab, we measure our goals through different inputs -
financial data, participant feedback, and qualitative marketing and
communications progress - and this results in a variety of forms of
data. The variety of data demands that, for this report, we create a
variety of visuals that we hope can sufficiently communicate our goals
and our progress. The data displayed in the following data
visualizations are an attempt at both enumerating and envisioning the
change our organization seeks to achieve. In coordination with teams
across Teaching Lab, we have leveraged our ongoing tracking of
organizational goals to produce the following quarterly report. As we
built the report, we've measured all that we can quantitatively and
translated that data to visuals, adding narrative where quantitative
measurement is not indicated.

### How:

This layered visualization and narrative description of our progress
toward our organizational goals is organized by organizational goal
area. Every goal area's data visualization or narrative is unique based
upon the progress metrics and measurements that are most appropriate to
that goal. For every goal, in addition to providing progress data, the
functional leader for that goal area has offered their assessment of
whether or not we are on track to reaching the goal before the end of
the fiscal year.

Taken individually, the goal area visualizations enable targeted
exploration of our progress in different functional areas. Taken
together, the measurement of these goals and progress measurements can
provide an overall assessment of Teaching Lab's progress meeting the
annual organizational goals that bring us closer to our mission of
fundamentally shifting the paradigm of professional learning for
educational equity.

# Goal 1: Expand Reach

> **Goal: 10,000 educators reached, serving over 700,000 students**

We have exceeded our reach goal in Q1 by reaching 10, 719 educators; at
648,725 students reached, we need to grow to impact at least 51,275 more
students in the remainder of FY23.

<center>

```{r student-reach, fig.dim = c(7, 9)}
# colours <- MetBrewer::met.brewer("Tiepolo", n = 20)
# 
# educators_students <- tibble::tibble(
#   x = c(rep(1, 10000), rep(2, 100000)),
#   y = c(sample(1:70000, 10000, replace = TRUE), sample(1:900000, 100000))
# ) |>
#   mutate(
#     alpha = sample(1:3 / 1000, length(x), replace = TRUE),
#     label = sample(c(LETTERS, letters), length(x), replace = TRUE),
#     color = sample(colours, length(x), replace = TRUE),
#     # transition = c(rep(1, 1000), rep(2, 70000)),
#     y = jitter(y, amount = 1),
#     x = jitter(x, amount = 0.5)
#   )
# 
# # educators_students_text <- tibble::tibble(x = c(1, 2),
# #                                           y = c(10000, 700000),
# #                                           text = c("10,000\neducators", "700,000\nstudents"))
# 
# ggplot(educators_students, aes(x, y, label = label, color = color, alpha = alpha)) +
#   geom_text(family = "WeePeople", size = 6) +
#   # transition_states(
#   #   transition,
#   #   transition_length = 2,
#   #   state_length = 1
#   # ) +
#   # enter_fade() +
#   # exit_shrink() +
#   # ease_aes('sine-in-out') +
#   scale_color_identity() +
#   scale_x_continuous(
#     breaks = 1:2,
#     labels = c("10,000\neducators", "700,000\nstudents")
#   ) +
#   theme_void() +
#   theme(
#     legend.position = "none",
#     # plot.background = element_rect(fill = "gray20"),
#     plot.title = element_text(color = "black", hjust = 0.5, face = "bold", family = "Fira Sans"),
#     plot.subtitle = element_text(color = "black", hjust = 0.5, face = "italic", family = "Fira Sans"),
#     axis.text.x = element_text(
#       color = "black", family = "Open Sans",
#       margin = margin(10, 0, 20, 0)
#     )
#   )

# ggplot(educators_students, aes(x = fake_x, y = fake_nums)) +
#   geom_col(aes(fill = fake_text)) +
#   geom_text(aes(label = fake_text), vjust = -0.5) +
#   scale_fill_manual(values = c("black", "#04abeb")) +
#   theme_void() +
#   theme(legend.position = "none")

gen_rev <- tibble::tibble(
  goal = c(10000, 700000),
  achieved = c(10719, 648725),
  labels = c("10,000 educators", "700,000 students")
)

ggplot(gen_rev) +
  geom_col(aes(x = labels, y = goal), fill = "gray") +
  geom_col(aes(x = labels, y = achieved), fill = "#04abeb", alpha = 0.75) +
  geom_text(aes(
    x = labels, y = goal,
    label = paste0("Goal: ", prettyNum(goal, big.mark = ",", scientific = FALSE))
  ),
  color = "gray55",
  vjust = -0.65,
  hjust = ifelse(gen_rev$labels == "10,000 educators" & gen_rev$goal == 10000, 
                 1.75, 
                 0.5),
  fontface = "bold"
  ) +
  geom_text(aes(
    x = labels, y = achieved,
    label = paste0("Achieved: ", prettyNum(achieved, big.mark = ",", scientific = FALSE))
  ),
  color = "#04abeb",
  vjust = -0.65,
  fontface = "bold"
  ) +
  theme_void() +
  theme(legend.position = "none",
        axis.text.x = element_text(face = "bold", color = "black", vjust = 2))
```

</center>

# Goal 2: Advance Educational Equity

> **Goal: 10% improvement between beginning and end of year in teacher
> equitable mindsets.**

Currently 62% of teachers demonstrate equitable mindsets; we need to
grow to 72% demonstrating those mindsets in the remainder of FY23 to
meet our goal.

<center>

```{r educational-equity, fig.dim = c(7, 4)}
improvement_plot(
  y_axis_title = "", plot_title = "",
  pre = 62, post = 72, lim1 = 50, lim2 = 75
)
```

</center>

> **Goal: 10% improvement between beginning and end of year in CRSE
> practices.**

Currently 79% of teachers are implementing CRSE practices; we need to
grow to 89% of teachers implementing them in the remainder of FY23 to
meet our goal.

<center>

```{r crse-practices, fig.dim = c(7, 4)}
improvement_plot(
  y_axis_title = "", plot_title = "",
  pre = 79, post = 89, lim1 = 70, lim2 = 100
)
```

</center>

# Goal 3: Increase Teacher and Student Learning

> **Goal: 10% improvement between beginning and end of year in teacher
> content knowledge**

Currently, 49% of teachers demonstrate content knowledge; we need to
grow to 59% demonstrating content knowledge in the remainder of FY23.

<center>

```{r increase-teacher-student-learning-1, fig.dim = c(7, 7)}
improvement_plot(
  y_axis_title = "", plot_title = "",
  pre = 49, post = 59, lim1 = 40, lim2 = 65
)
```

</center>

> **Goal: 10% improvement between beginning and end of year in teacher
> practice**

Currently, 58% of teachers have made improvements in teacher practice;
we need to grow to 68% making improvements in teacher practice in the
remainder of FY23.

<center>

```{r increase-teacher-student-learning-2, fig.dim = c(7, 7)}
improvement_plot(
  y_axis_title = "", plot_title = "",
  pre = 58, post = 68, lim1 = 45, lim2 = 75
)
```

</center>

# Goal 4: Generate Revenue

> **Goal: Earned revenue: \$6M**

At \$5.99M, we've nearly met our FY23 revenue goal.

> **Goal: Philanthropy for internal operations: \$6.5M**

We generated \$2.93M in philanthropy in our first quarter; to meet our
goal, we need to generate an additional \$1.74M in the remainder of
FY23.

> **Goal: Philanthropy for programmatic delivery: \$2M**

We have exceeded our goal in our first quarter, generating \$5.585M
philanthropy for programmatic delivery in FY23.

> **Goal: Total Revenue: \$14.5M**

We have nearly met our goal in our first quarter, generating \$13.183M
in FY23.

> **Goal: Total Programmatic Delivery Revenue: \$8M**

We have exceeded our goal in our first quarter, generating \$10.785M in
revenue in FY23.

<center>

```{r generate-revenue, fig.dim = c(9, 9)}
gen_rev <- tibble::tibble(
  goal = c(6, 6.5, 2, 14.5, 8),
  achieved = c(5.199, 2.394, 5.585, 13.183, 10.785),
  labels = c("Earned revenue",
  "Philanthropy for internal operations",
  "Philanthropy for programmatic delivery",
  "Total Revenue",
  "Total Programmatic Delivery Revenue")
) |>
  mutate(labels = str_wrap(labels, width = 27),
         labels = factor(labels, levels = labels))

ggplot(gen_rev) +
  geom_col(aes(x = labels, y = goal), fill = "gray") +
  geom_col(aes(x = labels, y = achieved), fill = "#04abeb", alpha = 0.75) +
  geom_text(aes(
    x = labels, y = goal,
    label = paste0("Goal: $", goal, "M")
  ),
  color = "gray40",
  vjust = -0.65,
  fontface = "bold"
  ) +
  geom_text(aes(
    x = labels, y = achieved,
    label = paste0("Achieved: $", achieved, "M")
  ),
  color = "#04abeb",
  vjust = -0.65,
  fontface = "bold"
  ) +
  theme_void() +
  theme(legend.position = "none",
        axis.text.x = element_text(face = "bold", color = "black", vjust = 1.5))
```

</center>

# Goal 5: Be Responsive to Educators

## Teachers

> **Goal: Teacher NPS \> 50**

In our first quarter, we have earned a teacher NPS of 28; to achieve a
score of 50, we will need to earn at least 50 more 9 or 10 ratings
(assuming no further negative ratings).

<center>

```{r responsive-educators, fig.dim = c(14, 6)}
arrow_data <- tibble::tibble(
  x = c(1, 2),
  y = c(1, 1)
)

nps_plot_1 <- ggplot() +
  geom_circle(aes(x0 = 0, y0 = 0, r = 1, size = 5), color = "#04abeb") +
  geom_text(aes(x = 0, y = 0, label = "28"),
    fontface = "bold", size = 16, color = "#04abeb"
  ) +
  labs(title = "NPS Score for SY22-23 So Far (n = 123)") +
  theme_void() +
  theme(
    legend.position = "none",
    plot.title = element_text(hjust = 0.5, face = "bold", color = "#04abeb")
  )

nps_arrow_plot <- ggplot(arrow_data, aes(x = x, y = y)) +
  geom_line(arrow = arrow(length = unit(0.30, "cm"), ends = "last", type = "closed"), size = 3, color = "#04abeb") +
  theme_void()

nps_plot_1_2 <- ggplot() +
  geom_circle(aes(x0 = 0, y0 = 0, r = 1, size = 5), color = "#04abeb") +
  geom_text(aes(x = 0, y = 0, label = "50"),
    fontface = "bold", size = 16, color = "#04abeb"
  ) +
  labs(title = "NPS Goal Score for SY22-23") +
  theme_void() +
  theme(
    legend.position = "none",
    plot.title = element_text(hjust = 0.5, face = "bold",  color = "#04abeb")
  )

nps_plot_1 + nps_arrow_plot + nps_plot_1_2 +
  plot_layout(widths = c(2, 0.5, 2))
```

</center>

## Non-Teachers

> **Goal: Non-teacher NPS \> 50**

We exceeded this goal in our first quarter with a non-teacher NPS of 55.

<center>

```{r responsive-educators-2, fig.dim = c(7, 7)}
nps_plot_2 <- ggplot() +
  geom_circle(aes(x0 = 0, y0 = 0, r = 1, size = 5)) +
  geom_text(aes(x = 0, y = 0, label = "55"),
    fontface = "bold", size = 16
  ) +
  theme_void() +
  theme(legend.position = "none")

nps_plot_2
```

</center>

# Goal 6: Scale Front-line Delivery (facilitator/coach) Quality

> **Goal: \>80% of participants say about facilitators/coaches: "They
> seemed fully prepared for the session."**

We exceeded this goal in our first quarter with 94% of all participants
saying facilitators are fully prepared for the session (n=461) and
97.22% of all participants saying coaches are fully prepared for the
session (n=37).

> **Goal: \>80% of participants say about facilitators/coaches: "They
> effectively built a safe learning community."**

We exceeded this goal in our first quarter with 94% of all participants
saying facilitators effectively build a safe learning environment
(n=461) and 94.44% of all participants saying coaches effectively build
a safe learning environment (n=37).

> **Goal: \>80% of participants say about facilitators/coaches: "They
> made adjustments based on participants' needs."**

We exceeded this goal in our first quarter with 92% of all participants
saying facilitators made adjustments based on participants' needs
(n=461) and 94% of all participants saying coaches made adjustments
based on participants' needs (n = 37).

<center>

```{r front-line-quality, fig.dim = c(7, 7)}
session_survey <- qualtRics::fetch_survey(surveyID = "SV_djt8w6zgigaNq0C", 
                               verbose = FALSE)

### Just first facilitator reviews ###
facilitator_one_reviews <- session_survey |>
  dplyr::select(`They demonstrated deep knowledge of the content they facilitated` = Q8_1, 
                `They facilitated the content clearly` = Q8_2, 
                `They effectively built a safe learning community` = Q8_3, 
                `They were fully prepared for the session` = Q8_4, 
                `They responded to the group’s needs` = Q8_5) |>
  dplyr::mutate(dplyr::across(c(1:5), ~ readr::parse_number(.x)))

### Just second facilitator reviews ###
facilitator_two_reviews <- session_survey |>
  dplyr::select(`They demonstrated deep knowledge of the content they facilitated` = Q12_1, 
                `They facilitated the content clearly` = Q12_2, 
                `They effectively built a safe learning community` = Q12_3, 
                `They were fully prepared for the session` = Q12_4, 
                `They responded to the group’s needs` = Q12_5) |>
  dplyr::mutate(dplyr::across(c(1:5), ~ readr::parse_number(.x)))

coach_reviews <- session_survey |>
  dplyr::select(`They demonstrated deep knowledge of the content they coached (coaching)` = Q67_1, 
                `Their coaching is clear (coaching)` = Q67_2, 
                `They effectively built a safe learning environment (coaching)` = Q67_3, 
                `They seem fully prepared for the coaching sessions (coaching)` = Q67_4, 
                `They made necessary adjustments based on my needs (coaching)` = Q67_5) |>
  dplyr::mutate(dplyr::across(c(1:5), ~ readr::parse_number(.x)))

### All facilitator reviews by binding rows together ###
all_facilitator_reviews <- facilitator_one_reviews |>
  dplyr::bind_rows(facilitator_two_reviews, coach_reviews) |>
  pivot_longer(everything(), names_to = "Question", values_to = "Response") |>
  drop_na(Response) |>
  group_by(Question, Response) |>
  count() |>
  ungroup() |>
  group_by(Question) |>
  mutate(Percent = round(100* n/sum(n)),
         Question = str_wrap(Question, width = 45),
         Response = str_replace_all(as.character(Response), c("1" = "1 - Strongly disagree",
                                                              "2" = "2 - Disagree",
                                                              "3" = "3 - Neither agree nor disagree",
                                                              "4" = "4 - Agree",
                                                              "5" = "5 - Strongly agree")))

agree_strongly_agree_reviews <- tibble::tibble(achieved = map_chr(unique(all_facilitator_reviews$Question), 
        ~ agree_strongly_agree(data = all_facilitator_reviews, question = .x)),
        goal = rep(80, 10),
        labels = unique(all_facilitator_reviews$Question)) |>
  mutate(achieved = parse_number(achieved))

agree_strongly_agree_reviews |>
  filter(str_detect(labels, "prepared|safe learning|needs")) |>
  arrange(str_detect(labels, "coaching")) |>
  ggplot() +
  geom_col(aes(x = labels, y = goal), fill = "gray") +
  geom_col(aes(x = labels, y = achieved), fill = "#04abeb", alpha = 0.75) +
  geom_text(aes(
    x = labels, y = achieved,
    label = paste0("Achieved: ", achieved, "%")
  ),
  color = "black",
  hjust = "inward",
  fontface = "bold",
  size = 5
  ) +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  coord_flip() +
  theme_tl() +
  theme(legend.position = "none",
        axis.text.y = element_text(face = "bold", color = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())

# all_facilitator_reviews |>
  # filter(str_detect(Question, "prepared|safe learning|needs")) |>
#   ggplot(aes(x = Question, y = Percent, fill = Response)) +
#   geom_col(position = position_stack(reverse = TRUE)) +
#   geom_text(aes(label = ifelse(Percent > 4, paste0(Percent, "%"), "")),
#             position = position_stack(vjust = 0.5, reverse = TRUE),
#             fontface = "bold") +
#   coord_flip() +
#   scale_y_continuous(labels = scales::percent_format(scale = 1)) +
#   scale_fill_manual(values = tl_palette(color = "blue", n = 5)) +
#   labs(x = "", y = "", title = "% Responses to Goal Setting Feedback Survey") +
#   theme_tl() +
#   theme(legend.position = "bottom")
```

</center>

# Goal 7: Be a Learning Organization

> **100% of revisions to existing products/services and
> design/innovation of new products/services are done with user
> feedback**

> **Teaching Lab maintains cost of services at or below
> \$1,500/teacher/year**

> **Teaching Lab innovates new models that improve impact and
> cost-effectiveness and generate an ROI by Year 3 of initial innovation
> investment**

For our Writing Pathways and Adaptive PL innovations, TL team leaders
will track these goals in collaboration with pilot teacher
participants. 

For the Writing Pathway, this tracking begins with BOY surveys - which
are administered as teachers join the Writing Pathway pilot; growth data
will be available after EOY surveys are administered in May 2023.

An adoptive Adaptive PL pilot cohort launches 10/26 with a goal of
starting with at least 15 participants.

As this is year one of the initial innovation investment, Year 3 ROI
data is not yet available.

<center>

```{r learning-organization, fig.dim = c(7, 7)}
```

</center>

# Goal 8: Innovate to Improve the Model

> **Goal: 80% of innovations pursued in FY23 have indicators of client
> satisfaction and impact by the end of the year**

> **Goal: 80% of innovations are on track to generate revenue and a
> return on investment in FY25**

For our Writing Pathways and Adaptive PL innovations, TL team leaders
will track these goals in collaboration with pilot teacher
participants. 

For the Writing Pathway, this tracking begins with BOY surveys - which
are administered as teachers join the Writing Pathway pilot; growth data
will be available after EOY surveys are administered in May 2023.

An adoptive Adaptive PL pilot cohort launches 10/26 with a goal of
starting with at least 15 participants.

As the innovations are early in implementation, Year 5 revenue and ROI
data is not available.

<center>

```{r improve-model, fig.dim = c(7, 7)}

```

</center>

# Goal 9: Create a flexible and partnership-driven team structure

> **Goal: By the end of FY23, \>80% of Teaching Lab team members can
> explain the flexible project team structure**

73% of Teaching Lab team members say they can explain the flexible
project team structure; we need to grow to 80%, which represents
approximately 4 more team members saying they can explain the structure.

> **Goal: By the end of FY23, \>80% of Teaching Lab team members say,
> "the flexible project team structure is an improvement over how we
> previously organized our work."**

49% of Teaching Lab team members say the flexible team structure is an
improvement over how we previously organized our work; we need to grow
to 80%, which represents approximately 17 more team members saying the
structure is an improvement.

<center>

```{r create-flexible, fig.dim = c(7, 11)}
team_struct <- tibble::tibble(
  x = c(
    "% who say they are able to explain project team structure",
    "% who say structure is an improvement"
  ),
  goal = c(80, 80),
  achieved = c(73, 49)
) |>
  mutate(x = str_wrap(x, width = 30))

ggplot(team_struct) +
  geom_col(aes(x = x, y = goal), fill = "black") +
  geom_col(aes(x = x, y = achieved), fill = "#04abeb") +
  geom_text(aes(x = x, y = goal, 
                label = paste0("Goal: ", goal, "%")),
    vjust = -0.75,
    fontface = "bold",
    color = "black",
    size = 8
  ) +
  geom_text(aes(x = x, y = achieved, 
                label = paste0("Achieved: ", achieved, "%")),
    vjust = -0.75,
    fontface = "bold",
    color = "#04abeb",
    size = 8
  ) +
  theme_void() +
  theme(axis.text.x = element_text(face = "bold", vjust = 10, size = 13))
```

</center>

# Goal 10: Research becomes the way we do our work

> **Goal: 90% of partnerships collect and analyze Educator Surveys 2x/
> year**

We exceeded this goal in our first quarter with 100% of partnerships
collecting data for our Educator Surveys.

> **Goal: 90% of partnerships collect and analyze student data and
> teacher practice data relevant to their SOW and aligned to the FY23
> evaluation plan.**

We have not collected data on this goal in our first quarter.

<center>

```{r research-becomes, fig.dim = c(7, 7)}
educator_survey <- qualtRics::fetch_survey(surveyID = "SV_8vrKtPDtqQFbiBM",
                                           verbose = FALSE) |>
  filter(Finished == TRUE)

educator_survey |>
  group_by(Site) |>
  count(sort = T) |>
  ungroup() |>
  drop_na() |>
  gt::gt() |>
  data_color(
    columns = c(n),
    colors = scales::col_numeric(
      palette = paletteer::paletteer_d(
        palette = "ggsci::blue_material"
      ) |>
        as.character(),
      domain = NULL
    )
  ) |>
  tab_header(title = md("**100% of partners have completed diagnostic survey data collection this year**")) |>
  TeachingLab::gt_theme_tl() #|>
  # gtsave("ed_survey_count.png", path = tempdir(), zoom = 4)
```

</center>

# Goal 11: Create and sustain enabling conditions

> **Goal: At the end of the year, 80% of partners increase by at least 1
> rating category on at least 1 enabling condition on the PL Enabling
> Conditions scorecard**

No data for this goal is available, the data will be available at the
end of Q2 and Q4.

<!-- NOTE: Insert scorecard -->

<center>

```{r create-enable-conditions, fig.dim = c(7, 7)}

```

</center>

# Goal 12: Continue to become an antiracist organization

> **Goal: 80% of staff members say anti-racism is embedded into my work
> at Teaching Lab**

62% of team members say anti-racism is embedded into their work at
Teaching Lab; we need to reach \>80% of team members saying that,
representing approximately at least 10 additional Teaching Lab members
expressing their belief that anti-racism is embedded in their work.

> **Goal: 80% of staff members say they understand Teaching Lab's
> anti-racism principles and how we live them in our partnership design
> and service**

73% of team members say they understand Teaching Lab's anti-racism
principles and how we live them; we need to reach \>80%, representing
approximately 4 additional team members expressing their understanding.

> **Goal: "Staff NPS \>40"**

Our first quarter staff NPS is 30; we need to reach an NPS of \>40,
representing approximately five or more team members offering 9 or 10
ratings.

<center>

```{r antiracist-organization, fig.dim = c(7, 7)}
pulse_survey <- tibble::tibble(
  x = c(
    ">80% of staff members say anti-racism is embedded into my work at Teaching Lab",
    ">80% of staff members say they understand Teaching Lab's anti-racism principles and how we live them in our partnership design and service",
    "Staff NPS > 40"
  ),
  achieved = c(62, 73, 30),
  goal = c(80, 80, 40)
) |>
  mutate(x = str_wrap(x, width = 30))

ggplot(pulse_survey) +
  geom_col(aes(x = x, y = goal), fill = "black") +
  geom_col(aes(x = x, y = achieved), fill = "#04abeb") +
  geom_text(aes(x = x, y = goal, 
                label = paste0("Goal: ", goal, 
                               ifelse(x != "Staff NPS > 40", "%", ""))
                ),
    vjust = -0.5, 
    fontface = "bold", 
    color = "black", 
    size = 5
  ) +
  geom_text(aes(x = x, y = achieved, 
                label = paste0("Achieved: ", 
                               achieved, 
                               ifelse(x != "Staff NPS > 40", "%", ""))
                ),
    vjust = -0.5, 
    fontface = "bold", 
    color = "#04abeb", 
    size = 5
  ) +
  theme_void() +
  theme(axis.text.x = element_text(face = "bold", vjust = 1.2))
```

</center>

# Goal 13: Maintain financial sustainability

> **Goal: 80% of invoices are collected within 60 days**

We exceeded this goal, collecting 100% of our quarter one invoices in 60
days.

> **Goal: Earned Revenue/philanthropy ratio does not fall below
> 40%/60%**

We met this goal in our first quarter with a ratio of 40%/60% .

> **Goal: Profit margin remains at least 6%**

We have considerably exceeded this goal: Teaching Lab's first quarter
profit margin is 51%.

> **Goal: 4-6 month cash reserve**

We met this goal in our first quarter with a 6.23 month cash reserve.

> **Goal: Operational overhead cost (administrative and fundraising) is
> \<25%**

Operational overhead data is not available but will be generated later
in FY23 using project log data.

<center>

```{r financial-sustainability, fig.dim = c(7, 7)}
financial_sustainability_1 <- tibble::tibble(
  x = c("80% of invoices are collected within 60 days"),
  achieved = c(100),
  goal = c(80)
) |>
  mutate(x = str_wrap(x, width = "30"))

p1 <- ggplot(financial_sustainability_1) +
  geom_col(aes(x = x, y = goal), fill = "black") +
  geom_col(aes(x = x, y = achieved), fill = "#04abeb", alpha = 0.75) +
  geom_text(aes(x = x, y = achieved, 
                label = paste0("Achieved: ", 
                               achieved, 
                               "%")
                ),
    vjust = -1, 
    fontface = "bold", 
    color = "#04abeb", 
    size = 5
  ) +
  geom_text(aes(x = x, y = goal, 
                label = paste0("Goal: ", goal, 
                               "%")
                ),
    vjust = -0.75, 
    fontface = "bold", 
    color = "black", 
    size = 5
  ) +
  theme_void() +
  theme(axis.text.x = element_text(face = "bold", vjust = 1.2))

financial_sustainability_2 <- tibble::tibble(
  x = c("Profit margin remains at least 6%"),
  achieved = c(6.23),
  goal = c(6)
) |>
  mutate(x = str_wrap(x, width = "30"))

p2 <- ggplot(financial_sustainability_2) +
  geom_col(aes(x = x, y = goal), fill = "black") +
  geom_col(aes(x = x, y = achieved), fill = "#04abeb", alpha = 0.75) +
  geom_text(aes(x = x, y = goal, 
                label = paste0("Goal: ", goal, 
                               "%")
                ),
    vjust = -0.4, 
    fontface = "bold", 
    color = "black", 
    size = 5
  ) +
  geom_text(aes(x = x, y = achieved, 
                label = paste0("Achieved: ", 
                               achieved, 
                               "%")
                ),
    vjust = -1, 
    fontface = "bold", 
    color = "#04abeb", 
    size = 5
  ) +
  theme_void() +
  theme(axis.text.x = element_text(face = "bold", vjust = 1.2))

# financial_sustainability_3 <- tibble::tibble(
#   x = c(""),
#   achieved = c(6.23),
#   goal = c(6)
# )
# 
# p3 <- ggplot() +
#   geom_text(aes(x = 0, y = 0,
#                 label = "To be decided based\non project log results\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n\nOperational overhead cost \nadministrative and fundraising)\nis <25%"),
#             fontface = "bold") +
#   theme_void()

p1 + p2 #+ p3
```

</center>

# Goal 14: Online courses support partnership development

> **Goal: 80% of each open enrollment course is booked with participants
> Courses generate an NPS of 50**

We have not yet enrolled participants in our open enrollment courses.

<center>

```{r online-courses-support, fig.dim = c(7, 7)}

```

</center>

# Goal 15: Influence the field

> **Goal: "Teaching Lab engages in at least three (3)"large resource
> drops" w/ full communications plan focused on: CRSE, Foundational
> Literacy (k-8), 6-8 Math, and/or innovative PL (including the use of
> technology) and resources generate \>1,000 downloads"**

The Marketing & Communications team has focused in their first quarter
on collecting resources for Q2, Q3 and Q4 resource drops.

<center>

```{r influence-field, fig.dim = c(7, 7)}

```

</center>

# Goal 16: Operate efficiently and equitably

> **Goal: 80% of users say that organizational systems (monday.com,
> Canvas, Justworks, etc) increased their organizational collaboration,
> efficiency, or transparency**

We met our goal with some organizational systems in our first quarter
and posted an average of 73% of team members across tools saying the
tools increased their collaboration, efficiency or transparency.

The average broken out across tools is as follows:

-   Monday.com: 78%

-   Justworks: 72%

-   Expensify: 89%

-   Canvas: 52%.

> **Goal: 100% of leads and clients are tracked in the CRM, following
> business rules**

In our first quarter, 80% of our business opportunities without movement
are tracked within 30 days; 4% of our opportunities without movement are
tracked within 60 days, and 16% of our opportunities without movement
are tracked within 90 days.

> **Goal: 100% of earned revenue and philanthropic pipeline data is
> updated, usable and accurate by the end of each month**

100% of inputted earned revenue and philanthropic pipeline data is
updated, usable and accurate by the end of each month; additionally,
closed contracts at 100% are now updated by in the Monday board upon
receipt.

> **Goal: 90% of FTEs and PTEs agree that they "have the data or
> information I need to do my work right"**

In the first quarter, 70% of our FTEs and PTEs say that they have the
data or information they need to do their work right; we need to grow by
20% to meet this goal in FY23, representing approximately 11 additional
employees agreeing they have the data or information they need to do
their work right.

<center>

```{r operate-eff-equit, fig.dim = c(9, 9)}
efficiently_equitably <- tibble::tibble(x = c("80% of users say that organizational systems (monday.com, Canvas, Justworks, etc) increased their organizational collaboration, efficiency, or transparency",
  "100% of leads and clients are tracked in the CRM, following business rules",
  "100% of earned revenue and philanthropic pipeline data is updated, usable and accurate by the end of each month",
  "90% of FTEs and PTEs agree that they “have the data or information I need to do my work right”"),
  achieved = c(73, 90, 100, 70),
  goal = c(80, 100, 100, 90)
) |>
  mutate(x = str_wrap(x, width = 50))

efficiently_equitably <- efficiently_equitably[c(1, 4),]

ggplot(efficiently_equitably) +
  geom_col(aes(x = x, y = goal), fill = "black") +
  geom_col(aes(x = x, y = achieved), fill = "#04abeb") +
  geom_text(aes(x = x, y = goal, 
                label = ifelse(achieved != 100, paste0("Goal: ", goal, 
                               "%"), ""),
                color = ifelse(goal == 80, "black", "white")
                ),
    vjust = -0.5, 
    fontface = "bold", 
    color = "black",
    size = 4
  ) +
  geom_text(aes(x = x, y = achieved, 
                label = ifelse(achieved != 100, paste0("Achieved: ", 
                               achieved, 
                               "%"), ""),
                color = ifelse(goal == 80, "black", "white")
                ),
    vjust = -0.5, 
    fontface = "bold", 
    color = "#04abeb",
    size = 4
  ) +
  geom_text(aes(x = x, y = achieved, 
                label = ifelse(achieved == 100, paste0("Achieved: ", 
                               achieved, 
                               "%"), ""),
                color = ifelse(goal == 80, "black", "white")
                ),
    vjust = -0.5, 
    hjust = 0.7,
    fontface = "bold", 
    color = "#04abeb",
    size = 4
  ) +
  geom_text(aes(x = x, y = goal, 
                label = ifelse(achieved == 100, paste0("Goal: ", 
                               goal, 
                               "%"), "")
                ),
    vjust = -0.5, 
    hjust = -0.45,
    fontface = "bold", 
    color = "black",
    size = 4
  ) +
  theme_void() +
  theme(axis.text.x = element_text(face = "bold", vjust = 1.2),
        legend.position = "none")
```

</center>

# Goal 17: Team members receive meaningful feedback for growth throughout the year

> **Goal: 80% of FTEs and PTEs who engage in the PDS report, at each
> phase, that the process is clear and/or valuable**

Currently, 79% of Teaching Lab staff expressed that they receive
meaningful feedback for growth throughout the year across the metrics
that measure this sentiment, nearly meeting our FY23 goal in our first
quarter.

<center>

```{r meaningful-feedback, fig.dim = c(7, 12)}
meaningful_feedback <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1p_-Q6NpKUWuYJLZo_s7ppgJ-GDb3Nrvtj_wip6ZVeUk/edit#gid=422634022")

percents_meaningful_feedback <- meaningful_feedback |>
  select(where(is.numeric)) |>
  pivot_longer(everything(), names_to = "Question", values_to = "Response") |>
  drop_na(Response) |>
  group_by(Question, Response) |>
  count() |>
  ungroup() |>
  group_by(Question) |>
  mutate(Percent = 100* n/sum(n),
         Question = str_wrap(Question, width = 45),
         Response = str_replace_all(as.character(Response), c("1" = "1 - Strongly disagree",
                                                              "2" = "2 - Disagree",
                                                              "3" = "3 - Neither agree nor disagree",
                                                              "4" = "4 - Agree",
                                                              "5" = "5 - Strongly agree")))

agree_strongly_agree_meaningful <- tibble::tibble(achieved = map_chr(unique(percents_meaningful_feedback$Question), 
        ~ agree_strongly_agree(data = percents_meaningful_feedback, question = .x)),
        labels = str_wrap(unique(percents_meaningful_feedback$Question), width = 20),
        goal = rep(80, 12)
) |>
  mutate(achieved = readr::parse_number(achieved))

ggplot(agree_strongly_agree_meaningful) +
  geom_col(aes(x = labels, y = goal), fill = "gray") +
  geom_col(aes(x = labels, y = achieved), fill = "#04abeb", alpha = 0.75) +
  geom_text(aes(
    x = labels, y = achieved,
    label = paste0("Achieved: ", achieved, "%")
  ),
  color = "black",
  hjust = "inward",
  fontface = "bold",
  size = 5
  ) +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  coord_flip() +
  theme_tl() +
  theme(legend.position = "none",
        axis.text.y = element_text(face = "bold", color = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())
```

</center>
