---
title: "Example Report Comparing Content Types"
author: "Teaching Lab Monthly Facilitator Review"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  rmdformats::readthedown:
    css: styles.css
    self_contained: true # Other options are downcute, material, readthedown, html_clean, html_docco, lockdown, https://github.com/juba/rmdformats
    thumbnails: false
    lightbox: true
    gallery: false
    highlight: kate # Also can do tango
    number_sections: false
    includes:
      after_body: footer.html
---

```{r setup, echo = F, cache = F, include = F}
knitr::opts_chunk$set(echo = F, message = F, warning = F, fig.width = 16, fig.height = 10, width = 2000)
library(tidyverse)
library(lubridate)
library(ggiraph)
library(gt)
library(reactable)
library(reactablefmtr)
library(scales)
library(htmltools)
library(htmlwidgets)
library(glue)
library(here)
sheets_data <- read_rds(here("Data/google_sheets_data.rds"))

col <- colorRampPalette(c("#040404", "#04ABEB"))

# options(width = 2000) # Adjust the width 

theme_set(theme_minimal())
```

```{r echo = F}
htmltools::tagList(rmarkdown::html_dependency_font_awesome()) # Needed so fa's in footer will show
```

```{r}
teaching_lab_df <- read_rds(here("Data/original_df.rds")) # Read original data for column names

# There's Guidebooks, and GuideBooks so vector for later filter
guidebooks <- c("Guidebooks|GuideBooks")

not_state_level <- c("EL|IM|Guidebooks|GuideBooks") # Define those for which we should filter for later


```


# By Portfolio

An example of how each portfolio can be compared - the gray line represents the overall average and the extending segments to larger dots represent the distance from the overall mean to the actual mean of each portfolio.

```{r}
sorted_teaching_df <- teaching_lab_df %>%
  group_by(`Date for the session`) %>%
  mutate(pro_grouping = case_when(!str_detect(`Professional training session`, not_state_level) == T ~ "State-Level",
                                  str_detect(`Professional training session`, "IM") == T ~ "IM",
                                  str_detect(`Professional training session`, guidebooks) == T ~ "Guidebooks",
                                  str_detect(`Professional training session`, "EL") == T ~ "EL")) %>%
  drop_na(`How likely are you to recommend this professional learning to a colleague or friend?`,
          pro_grouping) %>%
  group_by(pro_grouping) %>%
  # Means before and after pandemic by type of training session
  mutate(grouped_means = mean(`How likely are you to recommend this professional learning to a colleague or friend?`, na.rm = T)) %>%
  mutate(pro_grouping = forcats::fct_reorder(pro_grouping, -grouped_means)) %>%
  ungroup() %>%
  # Means of before and after pandemic
  mutate(mean_score = mean(`How likely are you to recommend this professional learning to a colleague or friend?`)) %>%
  ungroup()

# Axis colors 
axis_colors <- rev(c("#040404", "#324D56", "#346475", "#04ABEB"))

# Make the graph aesthetics, theme, and limits
g <- ggplot(sorted_teaching_df, aes(
              x = fct_rev(pro_grouping), 
              y = `How likely are you to recommend this professional learning to a colleague or friend?`, 
              color = pro_grouping
  )) +
  scale_y_continuous(limits = c(0, 10), breaks = scales::breaks_pretty(n = 10)) +
  scale_color_manual(values = rev(col(4))) +
  coord_flip() +
  labs(x = "", y = "Likeliness to Recommend to a Friend or Colleague", title = "Comparing Scores Between Content Types") +
  theme(legend.position = "none",
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5, family = "Oswald"),
        plot.subtitle = element_text(hjust = 0.5, family = "Oswald"),
        panel.grid = element_blank(),
        axis.title.y = element_text(family = "Oswald"),
        axis.title.x = element_text(family = "Oswald"),
        axis.text.x = element_text(color = "#324D56", family = "Oswald", 
                                   margin = unit(c(0, 0, -0.2, 0), "cm"),
                                   vjust = 10),
        axis.text.y = element_text(color= axis_colors, family = "Oswald"),
        strip.text = element_text(family = "Oswald", size = 10),
        legend.text = element_text(family = "Oswald"),
        axis.ticks.x = element_line(size = 3, color = "#324D56", linetype = 2),
        axis.ticks.length.x = unit(0.2, "cm"))


# Graph with geoms applied for baselayer test
g + 
  geom_segment(
    aes(x = fct_rev(pro_grouping), xend = fct_rev(pro_grouping),
        y = mean_score, yend = grouped_means),
    show.legend = F,
    size = 0.8
  ) + 
  geom_jitter(size = 3, alpha = 0.1,
              height = 0.15, width = 0.28) +
  stat_summary(fun = mean, geom = "point", size = 5) +
  geom_hline(aes(yintercept = mean_score), color = "gray70")
```

# By Month

The above plot is now replicated without portfolio groupings for each month.

```{r}
sorted_monthly_teaching_df <- teaching_lab_df %>%
  mutate(Month = lubridate::month(`Date for the session`, label = T, abbr = F)) %>%
  group_by(Month) %>%
  mutate(grouped_means = mean(`How likely are you to recommend this professional learning to a colleague or friend?`, na.rm = T)) %>%
  ungroup() %>%
  mutate(mean_score = mean(`How likely are you to recommend this professional learning to a colleague or friend?`, na.rm = T)) %>%
  drop_na(Month) %>%
  mutate(Month = factor(Month, levels = c("July", "August", "September", "October", "November", "December", "January", "February", "March", "April", "May", "June"))) %>%
  arrange(Month)
```

```{r}
# Make the graph aesthetics, theme, and limits
g <- ggplot(sorted_monthly_teaching_df, aes(
              x = Month, 
              y = `How likely are you to recommend this professional learning to a colleague or friend?`, 
              color = Month
  )) +
  scale_y_continuous(limits = c(0, 10), breaks = scales::breaks_pretty(n = 10)) +
  scale_color_manual(values = rev(col(11))) +
  coord_flip() +
  labs(x = "", y = "Likeliness to Recommend to a Friend or Colleague", title = "Comparing Scores Just By Month") +
  theme(legend.position = "none",
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5, family = "Oswald"),
        plot.subtitle = element_text(hjust = 0.5, family = "Oswald"),
        panel.grid = element_blank(),
        axis.title.y = element_text(family = "Oswald"),
        axis.title.x = element_text(family = "Oswald"),
        axis.text.x = element_text(color = "#324D56", family = "Oswald", 
                                   margin = unit(c(0, 0, -0.2, 0), "cm"),
                                   vjust = 10),
        axis.text.y = element_text(color= axis_colors, family = "Oswald"),
        strip.text = element_text(family = "Oswald", size = 10),
        legend.text = element_text(family = "Oswald"),
        axis.ticks.x = element_line(size = 3, color = "#324D56", linetype = 2),
        axis.ticks.length.x = unit(0.2, "cm"))


# Graph with geoms applied for baselayer test
g + 
  geom_segment(
    aes(x = Month, xend = Month,
        y = mean_score, yend = grouped_means),
    show.legend = F,
    size = 0.8
  ) +
  geom_jitter(size = 3, alpha = 0.1,
              height = 0.15, width = 0.28) +
  stat_summary(fun = mean, geom = "point", size = 5) +
  geom_hline(aes(yintercept = mean(`How likely are you to recommend this professional learning to a colleague or friend?`, na.rm = T)), color = "gray70")
```


# By Portfolio by Month

Finally, taking a look at each portfolio in each month. The text automation here is limitless - I can make it say certain strings in each section, such as specifying the worst performer in x month is y portfolio with an average of n that is n less than the overall average $n_2$.

```{r echo = F}
sorted_monthly_portfolio_teaching_df <- teaching_lab_df %>%
  mutate(Month = lubridate::month(`Date for the session`, label = T, abbr = F)) %>%
  group_by(`Date for the session`) %>%
  mutate(pro_grouping = case_when(!str_detect(`Professional training session`, not_state_level) == T ~ "State-Level",
                                  str_detect(`Professional training session`, "IM") == T ~ "IM",
                                  str_detect(`Professional training session`, guidebooks) == T ~ "Guidebooks",
                                  str_detect(`Professional training session`, "EL") == T ~ "EL")) %>%
  drop_na(`How likely are you to recommend this professional learning to a colleague or friend?`,
          pro_grouping) %>%
  group_by(Month, pro_grouping) %>%
  # Means before and after pandemic by type of training session
  mutate(grouped_means = mean(`How likely are you to recommend this professional learning to a colleague or friend?`, na.rm = T)) %>%
  mutate(pro_grouping = forcats::fct_reorder(pro_grouping, -grouped_means)) %>%
  ungroup(pro_grouping) %>%
  # Means of before and after pandemic
  mutate(mean_score = mean(`How likely are you to recommend this professional learning to a colleague or friend?`)) %>%
  ungroup()
```

```{r}
g <- ggplot(sorted_monthly_portfolio_teaching_df, aes(
              x = fct_rev(pro_grouping), 
              y = `How likely are you to recommend this professional learning to a colleague or friend?`, 
              color = pro_grouping
  )) +
  facet_wrap( ~ Month) +
  scale_y_continuous(limits = c(0, 10), breaks = scales::breaks_pretty(n = 10)) +
  scale_color_manual(values = rev(col(4))) +
  coord_flip() +
  labs(x = "", y = "Likeliness to Recommend to a Friend or Colleague", title = "Comparing Scores By Portfolio and Month") +
  theme(legend.position = "none",
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5, family = "Oswald"),
        plot.subtitle = element_text(hjust = 0.5, family = "Oswald"),
        panel.grid = element_blank(),
        axis.title.y = element_text(family = "Oswald"),
        axis.title.x = element_text(family = "Oswald"),
        axis.text.x = element_text(color = "#324D56", family = "Oswald", 
                                   margin = unit(c(0, 0, -0.2, 0), "cm"),
                                   vjust = 10),
        axis.text.y = element_text(color= axis_colors, family = "Oswald"),
        strip.text = element_text(family = "Oswald", size = 10),
        legend.text = element_text(family = "Oswald"),
        axis.ticks.x = element_line(size = 3, color = "#324D56", linetype = 2),
        axis.ticks.length.x = unit(0.2, "cm"))


# Graph with geoms applied for baselayer test
g + 
  geom_segment(
    aes(x = fct_rev(pro_grouping), xend = fct_rev(pro_grouping),
        y = mean_score, yend = grouped_means),
    show.legend = F,
    size = 0.8
  ) + 
  geom_jitter(size = 3, alpha = 0.1,
              height = 0.15, width = 0.28) +
  stat_summary(fun = mean, geom = "point", size = 5) +
  geom_hline(aes(yintercept = mean_score), color = "gray70")
```







