---
title: "list_sites_know_assess"
author: "Duncan Gates"
date: "1/11/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(googlesheets4)

surveys <- surveymonkey::browse_surveys() %>%
  dplyr::mutate(responses = map(id, ~ surveymonkey::fetch_survey_obj(id = .x)$`response_count`))

surveys_final <- surveys %>%
  dplyr::mutate(responses = as.numeric(responses)) %>%
  dplyr::filter(responses > 0 & str_detect(title, "ELA|Math")) %>%
  dplyr::arrange(title)

all_sites <- read_sheet("https://docs.google.com/spreadsheets/d/11jlo9UeWxZGwunhDb24hZBwAKc5b8ZKM9AYNWZaUyZY/edit#gid=0",
                        sheet = 1,
                        range = "C3:C",
                        col_names = "Site")
##### Not necessary right now at least #####
# sites <- all_sites$Site %>%
#   purrr::keep( ~ !str_detect(.x, "Rochester")) %>%
#   append("Rochester City School District, NY") %>%
#   sort()
# 
# sites %>% 
#   clipr::write_clip()
####################################################

get_sites_to_clip <- function(id) {
  
  survey <- surveymonkey::fetch_survey_obj(id) %>%
    surveymonkey::parse_survey()
  
  school_pull <- colnames(survey) %>%
    purrr::keep( ~ stringr::str_detect(.x, "your site|Your site") & !stringr::str_detect(.x, "Other"))
  
  survey_sites <- survey %>%
    dplyr::pull(school_pull) %>%
    levels()
  
  sites <- all_sites$Site
  
  if (length(setdiff(sites, survey_sites)) == 0) {
    print("All sites in master list are in this survey")
  } else {
    print("Sites copied to clipboard")
    setdiff(sites, survey_sites) %>%
      clipr::write_clip()
  }
  # Print extra sites in survey to console
  if (length(setdiff(survey_sites, sites)) > 0) {
    print("Whoops! Extra sites listed below")
    print(tibble::as_tibble(setdiff(survey_sites, sites)))
  }
  
}
```

## Educator Survey

```{r}
get_sites_to_clip(306944493)
```


## Course Survey

```{r}
get_sites_to_clip(308116695)
```

## Session Survey

```{r}
get_sites_to_clip(308115193)
```

##  ELA EL: Bootcamp - ALL Block (3-5)

```{r}
get_sites_to_clip(317612750)
```

## ELA Foundational Skills: Cycle of Inquiry 2: Using Data to Inform Foundational Skills Instruction

```{r}
get_sites_to_clip(317871223)
```

## ELA General: Cycle of Inquiry - Complex Text

```{r}
get_sites_to_clip(311404498)
```

## ELA General: Cycle of Inquiry - Speaking & Listening

```{r}
get_sites_to_clip(315708558)
```

## ELA: Bootcamp - Foundational Skills Bootcamp Skills (K-2)

```{r}
get_sites_to_clip(309842602)
```

## ELA: Bootcamp - General

```{r}
get_sites_to_clip(309800566)
```

##  ELA: CRSE PLC

```{r}
get_sites_to_clip(312484554)
```

## ELA: Cycle of Inquiry - Curriculum Flex Foundational Skills

```{r}
get_sites_to_clip(314564825)
```

##  ELA: Guidebooks Diverse Learners Bootcamp - Leader

```{r}
get_sites_to_clip(311069987)
```

##  ELA: Guidebooks Diverse Learners Bootcamp - Teacher

```{r}
get_sites_to_clip(310008951)
```

##  ELA: Guidebooks Diverse Learners Bootcamp Writing

```{r}
get_sites_to_clip(310775522)
```

##  ELA: Guidebooks Diverse Learners Cycle of Inquiry - Fluency

```{r}
get_sites_to_clip(310776199)
```

##  ELA: Guidebooks Diverse Learners Cycle of Inquiry - Vocabulary

```{r}
get_sites_to_clip(310776879)
```

##  ELA: HQIM & Enrichment

```{r}
get_sites_to_clip(310009771)
```

## ELA: School Leader Coaching Series

Not sure what's going on here, doesn't seem to be done yet. Doesn't need to be done.

```{r eval = F}
# get_sites_to_clip(316752660)
```

##  School Leaders: ELA

```{r}
get_sites_to_clip(312485414)
```

##  Math: Accelerating Learning

```{r}
get_sites_to_clip(310768681)
```

##  Math: Accelerating Learning - EIC

```{r}
get_sites_to_clip(313784149)
```

##  Math: Bootcamp

```{r}
get_sites_to_clip(309842333)
```


##  Math: Bootcamp - EIC

Nothing to be done here, just EIC and District 11.

##  Math: Cycle of Inquiry I - Eliciting Student Thinking

```{r}
get_sites_to_clip(311433379)
```

## Math: Cycle of Inquiry II - Making Math Visible

```{r}
get_sites_to_clip(316733968)
```

##  Math: Cycle of Inquiry V- Sequencing and Connecting Representations

```{r}
get_sites_to_clip(311404789)
```
